---
title: "Fig. 3 Increasing injection time on DIA LIT methods"
---

# **Fig. 5 Improvement of the Number of Points Across Chromatographic Peaks**

Distribution of numbers of points across a peak by using Whisper100TM 20 SPD with DIA-LIT-based methods on Rapid, Normal, and Enhanced scanning modes and Whisper100TM 40 SPD with DIA-LIT-based methods on Turbo, Rapid, and Normal scanning modes on 1, 5, and 10 ng input material.

# Load packages

```{r}
library("tidyverse")
library("psych")
library("pheatmap")
library("ggpubr")
library("patchwork")
library("ghibli")
library("reprex")
library("ggh4x")
library("ggplot2")
```

The path to every folder used is stored to keep everything compact. PPP data is stored in the folder located in pp_path . To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r}
pp_path <- "C:/Users/lukwolt/Documents/R/Points_across_a_peak/"
```

# Figure A

Distribution of numbers of points across a peak by using Whisper100TM 20 SPD with DIA-LIT-based methods on Rapid, Normal, and Enhanced scanning modes and Whisper100TM 40 SPD with DIA-LIT-based methods on Turbo, Rapid, and Normal scanning modes on 1, 5, and 10 ng input material.

## Load data A

The data containing the number of points across the peak are exported separately from Spectronaut as tsv files. They are loaded in RStudio with the function `read.csv2()`.

1 ng

```{r}
pp_Turbo_40SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Turbo_DIA_1ng_40SPD_1CV.tsv"), sep = "/")
pp_Turbo_40SPD_1$indiv <- "Turbo_40SPD_1_"

pp_Rapid_40SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_1ng_40SPD_1CV.tsv"), sep = "/")
pp_Rapid_40SPD_1$indiv <- "Rapid_40SPD_1_"

pp_Normal_40SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_1ng_40SPD_1CV.tsv"), sep = "/")
pp_Normal_40SPD_1$indiv <- "Normal_40SPD_1_"

pp_Rapid_20SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_1ng_20SPD_1CV.tsv"), sep = "/")
pp_Rapid_20SPD_1$indiv <- "Rapid_20SPD_1_"

pp_Normal_20SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_1ng_20SPD_1CV.tsv"), sep = "/")
pp_Normal_20SPD_1$indiv <- "Normal_20SPD_1_"

pp_Enhanced_20SPD_1 <- read.csv2(paste0(pp_path, "PPP_LIT_Enhanced_DIA_1ng_20SPD_1CV.tsv"), sep = "/")
pp_Enhanced_20SPD_1$indiv <- "Enhanced_20SPD_1_"
```

5 ng

```{r}
pp_Turbo_40SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Turbo_DIA_5ng_40SPD_1CV.tsv"), sep = "/")
pp_Turbo_40SPD_5$indiv <- "Turbo_40SPD_5_"

pp_Rapid_40SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_5ng_40SPD_1CV.tsv"), sep = "/")
pp_Rapid_40SPD_5$indiv <- "Rapid_40SPD_5_"

pp_Normal_40SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_5ng_40SPD_1CV.tsv"), sep = "/")
pp_Normal_40SPD_5$indiv <- "Normal_40SPD_5_"

pp_Rapid_20SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_5ng_20SPD_1CV.tsv"), sep = "/")
pp_Rapid_20SPD_5$indiv <- "Rapid_20SPD_5_"

pp_Normal_20SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_5ng_20SPD_1CV.tsv"), sep = "/")
pp_Normal_20SPD_5$indiv <- "Normal_20SPD_5_"

pp_Enhanced_20SPD_5 <- read.csv2(paste0(pp_path, "PPP_LIT_Enhanced_DIA_5ng_20SPD_1CV.tsv"), sep = "/")
pp_Enhanced_20SPD_5$indiv <- "Enhanced_20SPD_5_"
```

10 ng

```{r}
pp_Turbo_40SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Turbo_DIA_10ng_40SPD_1CV.tsv"), sep = "/")
pp_Turbo_40SPD_10$indiv <- "Turbo_40SPD_10_"

pp_Rapid_40SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_10ng_40SPD_1CV.tsv"), sep = "/")
pp_Rapid_40SPD_10$indiv <- "Rapid_40SPD_10_"

pp_Normal_40SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_10ng_40SPD_1CV.tsv"), sep = "/")
pp_Normal_40SPD_10$indiv <- "Normal_40SPD_10_"

pp_Rapid_20SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Rapid_DIA_10ng_20SPD_1CV.tsv"), sep = "/")
pp_Rapid_20SPD_10$indiv <- "Rapid_20SPD_10_"

pp_Normal_20SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Normal_DIA_10ng_20SPD_1CV.tsv"), sep = "/")
pp_Normal_20SPD_10$indiv <- "Normal_20SPD_10_"

pp_Enhanced_20SPD_10 <- read.csv2(paste0(pp_path, "PPP_LIT_Enhanced_DIA_10ng_20SPD_1CV.tsv"), sep = "/")
pp_Enhanced_20SPD_10$indiv <- "Enhanced_20SPD_10_"
```

## Colnames A

With the function `colnames()` the data frame was named correctly.

```{r}
colnames(pp_Turbo_40SPD_1) <- colnames(pp_Turbo_40SPD_5) <- 
colnames(pp_Turbo_40SPD_10) <-  colnames(pp_Rapid_40SPD_1) <- 
colnames(pp_Rapid_40SPD_5) <- colnames(pp_Rapid_40SPD_10) <-  
colnames(pp_Normal_40SPD_1) <- colnames(pp_Normal_40SPD_5) <- 
colnames(pp_Normal_40SPD_10) <- colnames(pp_Rapid_20SPD_1) <- 
colnames(pp_Rapid_20SPD_5) <- colnames(pp_Rapid_20SPD_10) <-  
colnames(pp_Normal_20SPD_1) <- colnames(pp_Normal_20SPD_5) <-
colnames(pp_Normal_20SPD_10) <-  colnames(pp_Enhanced_20SPD_1) <- colnames(pp_Enhanced_20SPD_5) <- colnames(pp_Enhanced_20SPD_10) <- 
c("Points_per_Peaks", "indiv")
```

## Join A

Data frames containing PPP are combined with the function `rbind()`.

```{r}
pp <- rbind(
            pp_Turbo_40SPD_1, pp_Turbo_40SPD_5, pp_Turbo_40SPD_10, 
            pp_Rapid_40SPD_1, pp_Rapid_40SPD_5, pp_Rapid_40SPD_10, 
            pp_Normal_40SPD_1, pp_Normal_40SPD_5, pp_Normal_40SPD_10,
            pp_Rapid_20SPD_1, pp_Rapid_20SPD_5, pp_Rapid_20SPD_10,
            pp_Normal_20SPD_1, pp_Normal_20SPD_5, pp_Normal_20SPD_10, 
            pp_Enhanced_20SPD_1, pp_Enhanced_20SPD_5, pp_Enhanced_20SPD_10)
```

The number of samples per day, the injection time and the scanning mode are added to the data frame and the function `factor()` is used to arrange them.

```{r}
pp$input <- NA
pp$input[grepl("1_", pp$indiv)] <- "1 ng"
pp$input[grepl("5_", pp$indiv)] <- "5 ng"
pp$input[grepl("10_", pp$indiv)] <- "10 ng"
pp$input <- factor(pp$input, levels = unique(pp$input))

pp$IT <- NA
pp$IT[grepl("20SPD", pp$indiv)] <- "20 SPD"
pp$IT[grepl("40SPD", pp$indiv)] <- "40 SPD"
pp$IT <- factor(pp$IT, levels = c("40 SPD", "20 SPD"))

pp$method <- NA
pp$method[grepl("Turbo", pp$indiv)] <- "Turbo"
pp$method[grepl("Rapid", pp$indiv)] <- "Rapid"
pp$method[grepl("Normal", pp$indiv)] <- "Normal"
pp$method[grepl("Enhanced", pp$indiv)] <- "Enhanced"
pp$method <- factor(pp$method, levels = c("Turbo", "Rapid", "Normal", "Enhanced"))

```

## Plot A

For the violin plot, the data from 20 SPD and 40 SPD were combined with patchwork. So two different plots were created and the combined to `figure5a`. For both `geom_violin()` was used. The function `facet_grid()` separates the data into injection time and scanning mode. `scale_fill_manual()`, `labs()` and `theme()` have just aesthetic effects. Further a logarithm scale was used for this plot.

```{r}
palette1 <-c("#C8F5FF", "#75CFFF", "#B3E4FF") 

plot_40SPD <- pp %>%
  filter(IT == "40 SPD") %>% 
  ggplot(aes(x = input, y = Points_per_Peaks,
             fill = as.factor(indiv)))+
  scale_y_log10()+
  geom_violin(draw_quantiles = 0.5) +
  scale_fill_manual(values = rep(palette1,3)) +
  facet_grid(IT ~ method)+
  geom_hline(yintercept = 6,
             linetype = "dashed") +
  labs(title = "A")+
  theme(legend.position = "none",
        axis.text = element_text(size = 24),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.margin = margin(t = 20,  
                             r = 50,
                             b = 20,
                             l = 10),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.1))
palette2 <- c("#00E5E6", "#009999", "#00CCCC")

plot_20SPD <- pp %>%
  filter(IT == "20 SPD") %>% 
  ggplot(aes(x = input, y = Points_per_Peaks,
             fill = as.factor(indiv)))+
  geom_violin(draw_quantiles = 0.5)+
  scale_y_log10() +
  scale_fill_manual(values = rep(palette2,3)) +
  facet_grid(IT ~ method) +
  geom_hline(yintercept = 6,
             linetype = "dashed") +
  labs(x = "Input",
       y = "Points across a peak") +
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.margin = margin(t = 15,  
                             r = 50,
                             b = 10,
                             l = 10))

limit <- 10^c(min(c(layer_scales(plot_40SPD)$y$get_limits(), 
                   layer_scales(plot_20SPD)$y$get_limits())),
              max(c(layer_scales(plot_40SPD)$y$get_limits(),
                   layer_scales(plot_20SPD)$y$get_limits())))
```

Plot_40SPD and Plot_20SPD are combined using patchwork to create figure 5a.

```{r}
figure5a <- (plot_40SPD + 
    scale_y_log10(limits = limit,
                   breaks = c(3, 6, 10, 30))+
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()))/
  (plot_20SPD + 
     scale_y_log10(limits = limit,
                   breaks = c(3, 6, 10, 30))+
     theme(axis.title.y = element_text(hjust = -1.8, vjust = 1)))
figure5a
```

# Figure B

Comparison of the number of precursors with a number of points across a peak equal to or greater than 6 on DIA-LIT-based method on Turbo, Rapid, and Normal scanning mode with different input material (1 ng, 5 ng, and 10 ng of tryptic HeLa lysate) on WhisperTM 100 40 SPD and on Rapid, Normal, and Enhanced scanning mode with different input material (1 ng, 5 ng, and 10 ng of tryptic HeLa lysate) on WhisperTM 100 20 SPD.

To create a stacked barplot, the data frame is separated in two different groups. `temp2` includes all peptides with at least six points across the peak. `temp1` all the others. Both are combined in `temp` with `rbind()`.

```{r}
pp$acc <- pp$Points_per_Peaks >= 6

temp1 <- pp %>% 
  group_by(indiv, IT, input, method) %>% 
  summarise(n_prec = sum(!is.na(Points_per_Peaks)))

temp2 <- pp %>% 
  group_by(indiv, IT, input, method) %>% 
  summarise(n_acc = sum(acc))

temp1$Precursors <- "< 6"
temp2$Precursors <- "\U2265 6"

colnames(temp1)[5] <- "n"
colnames(temp2)[5] <- "n"

temp1$n <- temp1$n - temp2$n

temp <- rbind(temp2, temp1)

temp$Precursors <- factor(temp$Precursors, 
                         levels = c("< 6", "\U2265 6"))

id_pr_40SPD <- temp %>% 
  filter(IT == "40 SPD" ) %>% 
  ggplot(aes(x = method, y = n/4, fill = Precursors, group = method)) +
  geom_col() +
  theme_bw() +
  facet_grid(IT ~ input) +
  labs(x = "Scanning mode",
       y = "Precursors number",
       title = "B",
       fill = "Points across a peak")+
  scale_fill_manual(values = c("grey82", "#ff3030"))+
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.095),
        axis.title = element_blank(),
        axis.text = element_text(size = 24),
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        legend.title = element_text(size = 27, vjust = 1.3),
        legend.text = element_text(size = 22),
        legend.position = "top")

id_pr_20SPD <- temp %>% 
  filter(IT == "20 SPD" ) %>% 
  ggplot(aes(x = method , y = n/4, fill = Precursors, group = method)) +
  geom_col() +
  theme_bw() +
  facet_grid(IT ~ input) +
  labs(x = "Scanning mode",
       y = "Precursors number")+
  scale_fill_manual(values = c("grey82", "#ff3030"))+
  theme(axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 27),
        strip.background.x = element_blank(),
        strip.background = element_rect(fill = "#E5E4F7"),
        strip.text.x = element_blank(),
        axis.title.x = element_text(vjust = -1),
        legend.position = "none")

limit <- c(min(c(layer_scales(id_pr_40SPD)$y$get_limits(),
                 layer_scales(id_pr_20SPD)$y$get_limits())),
           max(c(layer_scales(id_pr_40SPD)$y$get_limits(),
                 layer_scales(id_pr_20SPD)$y$get_limits()))+500)
figure5b <-
 (id_pr_40SPD +
    theme(axis.title = element_blank())+
    scale_y_continuous(limits = limit))/
 (id_pr_20SPD +
    theme(axis.title.y = element_text(hjust = -2.15,
                                      vjust = 3.5))+
    scale_y_continuous(limits = limit))
```

# Plot A and B

Plot 5A and 5B are combined using patchwork to create figure 5 and save it as pdf.

```{r}
figure5 <- wrap_plots(figure5a,figure5b, nrow = 2)

cairo_pdf(filename = "Fig. 5 Improvement of the Number of Points Across Chromatographic Peaks.pdf", width = 16.67, height = 18.75,)
figure5 
dev.off()
```
