---
title: "Fig. 4 Comparison of Injection Time on Linear Ion Trap Mass Analyzer."
---

# Load packages

```{r}
library("tidyverse")
library("psych")
library("pheatmap")
library("ggpubr")
library("patchwork")
library("ghibli")
library("reprex")
library("ggh4x")
library("ggplot2")
```

# **Fig. 4 Comparison of Injection Time on Linear Ion Trap Mass Analyzer**

Comparison of the number of identified peptides on DIA-LIT-based method on Turbo, Rapid, and Normal scanning mode for WhisperTM 100 40 SPD from 1, 5, and 100 ng of tryptic HeLa lysate with different ITs at fixed 40 isolation windows. For Turbo scanning mode auto IT (16 ms), half of its auto-IT (8 ms), and the auto IT of Rapid (23 ms) and Normal (38 ms) were applied to determine the compromise between ions filling time and scanning speed of LIT on this mode. For Rapid scanning mode, the ITs of 23 ms and 38 ms suffice. On Normal scanning mode, only its auto-IT was applied for this comparison. Identified peptides with a coefficient of variation (CV) between 10% and 15% are colored with light red and those with a CV below 10% with dark red.

# Load data

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path . To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r}
lit_path <-"C:/Users/lukwolt/Documents/R/LIT/"
```

Data tables were exported from Spectronaut in csv files and need to be loaded in RStudio with the function `read.csv2()`.

8ms

```{r}
#Turbo_1ng_8ms
LITDIA_Turbo_1_8ms <- read.csv2(paste0(lit_path, "20220420_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_8ms.csv"))

#Turbo_5ng_8ms
LITDIA_Turbo_5_8ms <- read.csv2(paste0(lit_path, "20220420_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_8ms.csv"))

#Turbo_10ng_8ms
LITDIA_Turbo_10_8ms <- read.csv2(paste0(lit_path, "20220420_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_8ms.csv"))

#Turbo_100ng_8ms
LITDIA_Turbo_100_8ms <- read.csv2(paste0(lit_path, "20220420_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_8ms.csv"))

```

16ms

```{r}
#Turbo_1ng_16ms
LITDIA_Turbo_1_16ms <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))

#Turbo_5ng_16ms
LITDIA_Turbo_5_16ms <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))

#Turbo_10ng_16ms
LITDIA_Turbo_10_16ms <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))

#Turbo_100ng_16ms
LITDIA_Turbo_100_16ms <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

```

23ms 23ms_turbo

```{r}
#Turbo_1ng_23ms
LITDIA_Turbo_1_23ms <- read.csv2(paste0(lit_path, "20220219_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_23ms.csv"))

#Turbo_5ng_23ms
LITDIA_Turbo_5_23ms <- read.csv2(paste0(lit_path, "20220524_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_23ms.csv"))

#Turbo_10ng_23ms
LITDIA_Turbo_10_23ms <- read.csv2(paste0(lit_path, "20220524_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_23ms.csv"))

#Turbo_100ng_23ms
LITDIA_Turbo_100_23ms <- read.csv2(paste0(lit_path, "20220525_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_23ms.csv"))

```

23ms_rapid

```{r}
#Rapid_1ng_23ms
LITDIA_Rapid_1_23ms <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))

#Rapid_5ng_23ms
LITDIA_Rapid_5_23ms <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))

#Rapid_10ng_23ms
LITDIA_Rapid_10_23ms <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))

#Rapid_100ng_23ms
LITDIA_Rapid_100_23ms <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

```

38ms 38ms_turbo

```{r}
#Turbo_1ng_38ms
LITDIA_Turbo_1_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_38ms.csv"))

#Turbo_5ng_38ms
LITDIA_Turbo_5_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_38ms.csv"))

#Turbo_10ng_38ms
LITDIA_Turbo_10_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_38ms.csv"))

#Turbo_100ng_38ms
LITDIA_Turbo_100_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_38ms.csv"))

```

38ms_rapid

```{r}
#Rapid_1ng_38ms
LITDIA_Rapid_1_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_38ms.csv"))

#Rapid_5ng_38ms
LITDIA_Rapid_5_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_38ms_40SPD_File1.csv"))

#Rapid_10ng_38ms
LITDIA_Rapid_10_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_38ms.csv"))

#Rapid_100ng_38ms
LITDIA_Rapid_100_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_38ms.csv"))

```

38ms_normal

```{r}
#Normal_1ng_38ms
LITDIA_Normal_1_38ms <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))

#Normal_5ng_38ms
LITDIA_Normal_5_38ms <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))

#Normal_10ng_38ms
LITDIA_Normal_10_38ms <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))

#Normal_100ng_38ms
LITDIA_Normal_100_38ms <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

```

# Clean data tables

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It is also calculating the mean between the four replicates. Spectronaut does some imputation by default , but we want to keep missing values. Imputed values are replaced by NA. Peptides missing in more than one replicate are highlighted as *TRUE*.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  mutate(na_nbr = rowSums(is.na(y[-1]))) %>%
  mutate(mean_quantity = rowMeans(y[2:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("Highlighted ", sum(z$filtered), " peptide(s) found in less than ", ncol(y) -2, " replicates")
  
 return(z) }

```

The `filter_pep()` function is used for every data-set.

8ms clean

```{r}
LITDIA_Turbo_1_8ms <-  filter_pep(LITDIA_Turbo_1_8ms)
LITDIA_Turbo_5_8ms <-  filter_pep(LITDIA_Turbo_5_8ms)
LITDIA_Turbo_10_8ms <-  filter_pep(LITDIA_Turbo_10_8ms)
LITDIA_Turbo_100_8ms <-  filter_pep(LITDIA_Turbo_100_8ms)

```

16ms clean

```{r}
LITDIA_Turbo_1_16ms <-  filter_pep(LITDIA_Turbo_1_16ms)
LITDIA_Turbo_5_16ms <-  filter_pep(LITDIA_Turbo_5_16ms)
LITDIA_Turbo_10_16ms <-  filter_pep(LITDIA_Turbo_10_16ms)
LITDIA_Turbo_100_16ms <-  filter_pep(LITDIA_Turbo_100_16ms)

```

23ms clean 23ms turbo clean

```{r}
LITDIA_Turbo_1_23ms <-  filter_pep(LITDIA_Turbo_1_23ms)
LITDIA_Turbo_5_23ms <-  filter_pep(LITDIA_Turbo_5_23ms)
LITDIA_Turbo_10_23ms <-  filter_pep(LITDIA_Turbo_10_23ms)
LITDIA_Turbo_100_23ms <-  filter_pep(LITDIA_Turbo_100_23ms)

```

23ms rapid clean

```{r}
LITDIA_Rapid_1_23ms <-  filter_pep(LITDIA_Rapid_1_23ms)
LITDIA_Rapid_5_23ms <-  filter_pep(LITDIA_Rapid_5_23ms)
LITDIA_Rapid_10_23ms <-  filter_pep(LITDIA_Rapid_10_23ms)
LITDIA_Rapid_100_23ms <-  filter_pep(LITDIA_Rapid_100_23ms)

```

38ms clean 38ms turbo clean

```{r}
LITDIA_Turbo_1_38ms <-  filter_pep(LITDIA_Turbo_1_38ms)
LITDIA_Turbo_5_38ms <-  filter_pep(LITDIA_Turbo_5_38ms)
LITDIA_Turbo_10_38ms <-  filter_pep(LITDIA_Turbo_10_38ms)
LITDIA_Turbo_100_38ms <-  filter_pep(LITDIA_Turbo_100_38ms)

```

38ms rapid clean

```{r}
LITDIA_Rapid_1_38ms <-  filter_pep(LITDIA_Rapid_1_38ms)
LITDIA_Rapid_5_38ms <-  filter_pep(LITDIA_Rapid_5_38ms)
LITDIA_Rapid_10_38ms <-  filter_pep(LITDIA_Rapid_10_38ms)
LITDIA_Rapid_100_38ms <-  filter_pep(LITDIA_Rapid_100_38ms)

```

38ms normal clean

```{r}
LITDIA_Normal_1_38ms <-  filter_pep(LITDIA_Normal_1_38ms)
LITDIA_Normal_5_38ms <-  filter_pep(LITDIA_Normal_5_38ms)
LITDIA_Normal_10_38ms <-  filter_pep(LITDIA_Normal_10_38ms)
LITDIA_Normal_100_38ms <-  filter_pep(LITDIA_Normal_100_38ms)

```

# Number of identified peptides

Empty vectors to store the number of identified peptides in each replicates for each data-set are created.

```{r}
id_LITDIA_Turbo_1_8ms <- id_LITDIA_Turbo_5_8ms <- id_LITDIA_Turbo_10_8ms <- id_LITDIA_Turbo_100_8ms <- 
id_LITDIA_Turbo_1_16ms <- id_LITDIA_Turbo_5_16ms <- id_LITDIA_Turbo_10_16ms <- id_LITDIA_Turbo_100_16ms <- 
id_LITDIA_Turbo_1_23ms <- id_LITDIA_Turbo_5_23ms <- id_LITDIA_Turbo_10_23ms <- id_LITDIA_Turbo_100_23ms <-
id_LITDIA_Rapid_1_23ms <- id_LITDIA_Rapid_5_23ms <- id_LITDIA_Rapid_10_23ms <- id_LITDIA_Rapid_100_23ms <-
id_LITDIA_Turbo_1_38ms <- id_LITDIA_Turbo_5_38ms <- id_LITDIA_Turbo_10_38ms <- id_LITDIA_Turbo_100_38ms <-
id_LITDIA_Rapid_1_38ms <- id_LITDIA_Rapid_5_38ms <- id_LITDIA_Rapid_10_38ms <- id_LITDIA_Rapid_100_38ms <-
id_LITDIA_Normal_1_38ms <- id_LITDIA_Normal_5_38ms <- id_LITDIA_Normal_10_38ms <- id_LITDIA_Normal_100_38ms <-
  rep(NA, 4)
```

The identified peptides, that are not *NA*, are summed for each replicate and replace the empty vectors.

8ms 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_1_8ms[i-1] <- sum(!is.na(LITDIA_Turbo_1_8ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_5_8ms[i-1] <- sum(!is.na(LITDIA_Turbo_5_8ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_10_8ms[i-1] <- sum(!is.na(LITDIA_Turbo_10_8ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_100_8ms[i-1] <- sum(!is.na(LITDIA_Turbo_100_8ms[, i]))}
```

16ms 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_1_16ms[i-1] <- sum(!is.na(LITDIA_Turbo_1_16ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_5_16ms[i-1] <- sum(!is.na(LITDIA_Turbo_5_16ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_10_16ms[i-1] <- sum(!is.na(LITDIA_Turbo_10_16ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_100_16ms[i-1] <- sum(!is.na(LITDIA_Turbo_100_16ms[, i]))}
```

23ms 23ms turbo 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_1_23ms[i-1] <- sum(!is.na(LITDIA_Turbo_1_23ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_5_23ms[i-1] <- sum(!is.na(LITDIA_Turbo_5_23ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_10_23ms[i-1] <- sum(!is.na(LITDIA_Turbo_10_23ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_100_23ms[i-1] <- sum(!is.na(LITDIA_Turbo_100_23ms[, i]))}
```

23ms rapid 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_1_23ms[i-1] <- sum(!is.na(LITDIA_Rapid_1_23ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_5_23ms[i-1] <- sum(!is.na(LITDIA_Rapid_5_23ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_10_23ms[i-1] <- sum(!is.na(LITDIA_Rapid_10_23ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_100_23ms[i-1] <- sum(!is.na(LITDIA_Rapid_100_23ms[, i]))}
```

38ms 38ms turbo 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_1_38ms[i-1] <- sum(!is.na(LITDIA_Turbo_1_38ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_5_38ms[i-1] <- sum(!is.na(LITDIA_Turbo_5_38ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_10_38ms[i-1] <- sum(!is.na(LITDIA_Turbo_10_38ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Turbo_100_38ms[i-1] <- sum(!is.na(LITDIA_Turbo_100_38ms[, i]))}
```

38ms rapid 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_1_38ms[i-1] <- sum(!is.na(LITDIA_Rapid_1_38ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_5_38ms[i-1] <- sum(!is.na(LITDIA_Rapid_5_38ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_10_38ms[i-1] <- sum(!is.na(LITDIA_Rapid_10_38ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Rapid_100_38ms[i-1] <- sum(!is.na(LITDIA_Rapid_100_38ms[, i]))}
```

38ms normal 1ng

```{r}
for(i in 2:5){
  id_LITDIA_Normal_1_38ms[i-1] <- sum(!is.na(LITDIA_Normal_1_38ms[, i]))}
```

5ng

```{r}
for(i in 2:5){
  id_LITDIA_Normal_5_38ms[i-1] <- sum(!is.na(LITDIA_Normal_5_38ms[, i]))}
```

10ng

```{r}
for(i in 2:5){
  id_LITDIA_Normal_10_38ms[i-1] <- sum(!is.na(LITDIA_Normal_10_38ms[, i]))}
```

100ng

```{r}
for(i in 2:5){
  id_LITDIA_Normal_100_38ms[i-1] <- sum(!is.na(LITDIA_Normal_100_38ms[, i]))}
```

# Compute CV

The function below takes the data-sets, already filtered by `filter_pep()`, for entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our data-sets contain 4 replicates but some contains only 3. In this case an empty column is added with `compute_CV()` instead of a 4th replicate, to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the scanning mode, the injection time and the input are included afterwards.

8 ms

```{r}
LITDIA_Turbo_1_8ms_cv <- compute_CV(LITDIA_Turbo_1_8ms)
LITDIA_Turbo_1_8ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_1_8ms_cv$injection_time<- "8 ms"
LITDIA_Turbo_1_8ms_cv$input<- "1 ng"

LITDIA_Turbo_5_8ms_cv <- compute_CV(LITDIA_Turbo_5_8ms)
LITDIA_Turbo_5_8ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_5_8ms_cv$injection_time<- "8 ms"
LITDIA_Turbo_5_8ms_cv$input<- "5 ng"

LITDIA_Turbo_10_8ms_cv <- compute_CV(LITDIA_Turbo_10_8ms)
LITDIA_Turbo_10_8ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_10_8ms_cv$injection_time<- "8 ms"
LITDIA_Turbo_10_8ms_cv$input<- "10 ng"

LITDIA_Turbo_100_8ms_cv <- compute_CV(LITDIA_Turbo_100_8ms)
LITDIA_Turbo_100_8ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_100_8ms_cv$injection_time<- "8 ms"
LITDIA_Turbo_100_8ms_cv$input<- "100 ng"
```

16 ms

```{r}
LITDIA_Turbo_1_16ms_cv <- compute_CV(LITDIA_Turbo_1_16ms)
LITDIA_Turbo_1_16ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_1_16ms_cv$injection_time<- "16 ms"
LITDIA_Turbo_1_16ms_cv$input<- "1 ng"

LITDIA_Turbo_5_16ms_cv <- compute_CV(LITDIA_Turbo_5_16ms)
LITDIA_Turbo_5_16ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_5_16ms_cv$injection_time<- "16 ms"
LITDIA_Turbo_5_16ms_cv$input<- "5 ng"

LITDIA_Turbo_10_16ms_cv <- compute_CV(LITDIA_Turbo_10_16ms)
LITDIA_Turbo_10_16ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_10_16ms_cv$injection_time<- "16 ms"
LITDIA_Turbo_10_16ms_cv$input<- "10 ng"

LITDIA_Turbo_100_16ms_cv <- compute_CV(LITDIA_Turbo_100_16ms)
LITDIA_Turbo_100_16ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_100_16ms_cv$injection_time<- "16 ms"
LITDIA_Turbo_100_16ms_cv$input<- "100 ng"
```

23 ms

```{r}
LITDIA_Turbo_1_23ms_cv <- compute_CV(LITDIA_Turbo_1_23ms)
LITDIA_Turbo_1_23ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_1_23ms_cv$injection_time<- "23 ms"
LITDIA_Turbo_1_23ms_cv$input<- "1 ng"

LITDIA_Turbo_5_23ms_cv <- compute_CV(LITDIA_Turbo_5_23ms)
LITDIA_Turbo_5_23ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_5_23ms_cv$injection_time<- "23 ms"
LITDIA_Turbo_5_23ms_cv$input<- "5 ng"

LITDIA_Turbo_10_23ms_cv <- compute_CV(LITDIA_Turbo_10_23ms)
LITDIA_Turbo_10_23ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_10_23ms_cv$injection_time<- "23 ms"
LITDIA_Turbo_10_23ms_cv$input<- "10 ng"

LITDIA_Turbo_100_23ms_cv <- compute_CV(LITDIA_Turbo_100_23ms)
LITDIA_Turbo_100_23ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_100_23ms_cv$injection_time<- "23 ms"
LITDIA_Turbo_100_23ms_cv$input<- "100 ng"

LITDIA_Rapid_1_23ms_cv <- compute_CV(LITDIA_Rapid_1_23ms)
LITDIA_Rapid_1_23ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_1_23ms_cv$injection_time<- "23 ms"
LITDIA_Rapid_1_23ms_cv$input<- "1 ng"

LITDIA_Rapid_5_23ms_cv <- compute_CV(LITDIA_Rapid_5_23ms)
LITDIA_Rapid_5_23ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_5_23ms_cv$injection_time<- "23 ms"
LITDIA_Rapid_5_23ms_cv$input<- "5 ng"

LITDIA_Rapid_10_23ms_cv <- compute_CV(LITDIA_Rapid_10_23ms)
LITDIA_Rapid_10_23ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_10_23ms_cv$injection_time<- "23 ms"
LITDIA_Rapid_10_23ms_cv$input<- "10 ng"

LITDIA_Rapid_100_23ms_cv <- compute_CV(LITDIA_Rapid_100_23ms)
LITDIA_Rapid_100_23ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_100_23ms_cv$injection_time<- "23 ms"
LITDIA_Rapid_100_23ms_cv$input<- "100 ng"
```

38 ms

```{r}
LITDIA_Turbo_1_38ms_cv <- compute_CV(LITDIA_Turbo_1_38ms)
LITDIA_Turbo_1_38ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_1_38ms_cv$injection_time<- "38 ms"
LITDIA_Turbo_1_38ms_cv$input<- "1 ng"

LITDIA_Turbo_5_38ms_cv <- compute_CV(LITDIA_Turbo_5_38ms)
LITDIA_Turbo_5_38ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_5_38ms_cv$injection_time<- "38 ms"
LITDIA_Turbo_5_38ms_cv$input<- "5 ng"

LITDIA_Turbo_10_38ms_cv <- compute_CV(LITDIA_Turbo_10_38ms)
LITDIA_Turbo_10_38ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_10_38ms_cv$injection_time<- "38 ms"
LITDIA_Turbo_10_38ms_cv$input<- "10 ng"

LITDIA_Turbo_100_38ms_cv <- compute_CV(LITDIA_Turbo_100_38ms)
LITDIA_Turbo_100_38ms_cv$scanning_mode <- "Turbo"
LITDIA_Turbo_100_38ms_cv$injection_time<- "38 ms"
LITDIA_Turbo_100_38ms_cv$input<- "100 ng"

LITDIA_Rapid_1_38ms_cv <- compute_CV(LITDIA_Rapid_1_38ms)
LITDIA_Rapid_1_38ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_1_38ms_cv$injection_time<- "38 ms"
LITDIA_Rapid_1_38ms_cv$input<- "1 ng"

LITDIA_Rapid_5_38ms_cv <- compute_CV(LITDIA_Rapid_5_38ms)
LITDIA_Rapid_5_38ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_5_38ms_cv$injection_time<- "38 ms"
LITDIA_Rapid_5_38ms_cv$input<- "5 ng"

LITDIA_Rapid_10_38ms_cv <- compute_CV(LITDIA_Rapid_10_38ms)
LITDIA_Rapid_10_38ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_10_38ms_cv$injection_time<- "38 ms"
LITDIA_Rapid_10_38ms_cv$input<- "10 ng"

LITDIA_Rapid_100_38ms_cv <- compute_CV(LITDIA_Rapid_100_38ms)
LITDIA_Rapid_100_38ms_cv$scanning_mode <- "Rapid"
LITDIA_Rapid_100_38ms_cv$injection_time<- "38 ms"
LITDIA_Rapid_100_38ms_cv$input<- "100 ng"

LITDIA_Normal_1_38ms_cv <- compute_CV(LITDIA_Normal_1_38ms)
LITDIA_Normal_1_38ms_cv$scanning_mode <- "Normal"
LITDIA_Normal_1_38ms_cv$injection_time<- "38 ms"
LITDIA_Normal_1_38ms_cv$input<- "1 ng"

LITDIA_Normal_5_38ms_cv <- compute_CV(LITDIA_Normal_5_38ms)
LITDIA_Normal_5_38ms_cv$scanning_mode <- "Normal"
LITDIA_Normal_5_38ms_cv$injection_time<- "38 ms"
LITDIA_Normal_5_38ms_cv$input<- "5 ng"

LITDIA_Normal_10_38ms_cv <- compute_CV(LITDIA_Normal_10_38ms)
LITDIA_Normal_10_38ms_cv$scanning_mode <- "Normal"
LITDIA_Normal_10_38ms_cv$injection_time<- "38 ms"
LITDIA_Normal_10_38ms_cv$input<- "10 ng"

LITDIA_Normal_100_38ms_cv <- compute_CV(LITDIA_Normal_100_38ms)
LITDIA_Normal_100_38ms_cv$scanning_mode <- "Normal"
LITDIA_Normal_100_38ms_cv$injection_time<- "38 ms"
LITDIA_Normal_100_38ms_cv$input<- "100 ng"
```

# Join

Data frames containing CV are combined with the function `rbind()` and arranged with the function `factor()`.

```{r}
id_figure4 <- 
  rbind(LITDIA_Turbo_1_8ms_cv, LITDIA_Turbo_5_8ms_cv, LITDIA_Turbo_10_8ms_cv, 
        LITDIA_Turbo_100_8ms_cv, LITDIA_Turbo_1_16ms_cv, LITDIA_Turbo_5_16ms_cv, 
        LITDIA_Turbo_10_16ms_cv, LITDIA_Turbo_100_16ms_cv, LITDIA_Turbo_1_23ms_cv, 
        LITDIA_Turbo_5_23ms_cv, LITDIA_Turbo_10_23ms_cv, LITDIA_Turbo_100_23ms_cv, 
        LITDIA_Rapid_1_23ms_cv, LITDIA_Rapid_5_23ms_cv, LITDIA_Rapid_10_23ms_cv, 
        LITDIA_Rapid_100_23ms_cv, LITDIA_Turbo_1_38ms_cv, LITDIA_Turbo_5_38ms_cv, 
        LITDIA_Turbo_10_38ms_cv, LITDIA_Turbo_100_38ms_cv, LITDIA_Rapid_1_38ms_cv, 
        LITDIA_Rapid_5_38ms_cv, LITDIA_Rapid_10_38ms_cv, LITDIA_Rapid_100_38ms_cv, 
        LITDIA_Normal_1_38ms_cv, LITDIA_Normal_5_38ms_cv, LITDIA_Normal_10_38ms_cv,         LITDIA_Normal_100_38ms_cv)

id_figure4$scanning_mode %>% table()
id_figure4$injection_time %>% table()
id_figure4$input %>% table()

id_figure4$scanning_mode <- factor(id_figure4$scanning_mode, 
                          levels = unique(id_figure4$scanning_mode))

id_figure4$input <- factor(id_figure4$input, 
                          levels = unique(id_figure4$input))

id_figure4$injection_time <- factor(id_figure4$injection_time, 
                          levels = unique(id_figure4$injection_time))
```

A new column called "CV_filter" is added to identify peptides with a CV over 0.15 (1), CV between 0.1 and 0.15 (2) and CV under 0.1 (3).

```{r}
id_figure4$CV_filter <- NA
id_figure4$CV_filter[id_figure4$CV < 0.1] <- "3"
id_figure4$CV_filter[id_figure4$CV >= 0.1 & id_figure4$CV <= 0.15] <- "2"
id_figure4$CV_filter[id_figure4$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out and the number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method.

```{r}
id_figure4 <- id_figure4 %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(scanning_mode, injection_time, input, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))
id_figure4$id_S4[id_figure4$id_S4 == 0] <- NA 

id_figure4$mean_id <- rowMeans(id_figure4[5:8], na.rm = TRUE)
id_figure4$sd_id <- apply(id_figure4[5:8], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

# Plot

For

## Turbo

The position of the errorbars is determined.

```{r}
id_figure4$y_errorbar <- id_figure4$mean_id
id_figure4$y_errorbar[id_figure4$CV_filter == "1"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "1"] +
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
id_figure4$y_errorbar[id_figure4$CV_filter == "2"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
```

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot()`.The function `geom_errorbar()` was used to compute the length of the errorbars from the mean and the standard deviation. `facet_grid()` separates the data into injection time and scanning mode. `geom_col()`, `labs()`, `theme_bw()`, `theme()` and `scale_fill_manual()` have just aesthetic effects. With `scale_y_continuous()` a manual limit of the y axis was set.

```{r}
figure4_turbo <- id_figure4 %>% filter(input != "10 ng")  %>% filter(scanning_mode == "Turbo") %>% 
  ggplot(aes(x = input, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
 facet_grid(scanning_mode~injection_time)+
  labs(x = "",
       y = "Identified peptides",
       fill = "CV",
       title = "") +
  theme_bw() +
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.09),
    axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"))+
  scale_fill_manual(values = c("grey82", "#FF9090", "#FF3030"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 16000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)

```

## Rapid

The position of the errorbars is determined.

```{r}
id_figure4$y_errorbar <- id_figure4$mean_id
id_figure4$y_errorbar[id_figure4$CV_filter == "1"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "1"] +
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
id_figure4$y_errorbar[id_figure4$CV_filter == "2"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
```

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot()`.The function `geom_errorbar()` was used to compute the length of the errorbars from the mean and the standard deviation. `facet_grid()` separates the data into injection time and scanning mode. `geom_col()`, `labs()`, `theme_bw()`, `theme()` and `scale_fill_manual()` have just aesthetic effects. With `scale_y_continuous()` a manual limit of the y axis was set.

```{r}
figure4_rapid <- id_figure4 %>% filter(input != "10 ng")  %>% filter(scanning_mode == "Rapid") %>% 
  ggplot(aes(x = input, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
 facet_grid(scanning_mode~injection_time)+
  labs(x = "Input",
       y = "Identified peptides",
       fill = "CV",
       title = "") +
  theme_bw() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.09),
    axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"))+
scale_fill_manual(values = c("grey82", "#FF9090", "#FF3030"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 16000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)

```

## Normal

The position of the errorbars is determined.

```{r}
id_figure4$y_errorbar <- id_figure4$mean_id
id_figure4$y_errorbar[id_figure4$CV_filter == "1"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "1"] +
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
id_figure4$y_errorbar[id_figure4$CV_filter == "2"] <-
  id_figure4$y_errorbar[id_figure4$CV_filter == "2"]+
  id_figure4$y_errorbar[id_figure4$CV_filter == "3"]
```

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot()`.The function `geom_errorbar()` was used to compute the length of the errorbars from the mean and the standard deviation. `facet_grid()` separates the data into injection time and scanning mode. `geom_col()`, `labs()`, `theme_bw()`, `theme()` and `scale_fill_manual()` have just aesthetic effects. With `scale_y_continuous()` a manual limit of the y axis was set.

```{r}
figure4_normal <- id_figure4 %>% filter(input != "10 ng")  %>% filter(scanning_mode == "Normal") %>% 
  ggplot(aes(x = input, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
 facet_grid(scanning_mode~injection_time)+
  labs(x = "Input",
       y = "",
       fill = "CV",
       title = "") +
  theme_bw() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.09),
    axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"))+
scale_fill_manual(values = c("grey82", "#FF9090", "#FF3030"),
                  labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 16000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),  
                  width = 0.2,
                    size = 1)

```

# Join Turbo, Rapid, Normal

Figure4_turbo, Figure4_rapid and Figure4_normal are combined using patchwork to create figure 4 and save it as pdf.

```{r}
figure4 <- figure4_turbo/((figure4_rapid+figure4_normal)+plot_layout(widths = c(2,1)))
cairo_pdf(filename = "Fig. 4 Comparison of Injection Time on Linear Ion Trap Mass Analyzer.pdf", width = 20.83, height = 15.625)
figure4
dev.off()
```
