---
title: "Supporting figure S5 Proportions of peptides in the 3 CV groups with LIT and OT mass analyzer at different scanning speeds, resolution and inputs"
author: "Samuel Grégoire"
output:
  rmarkdown::github_document
---

Supporting figure S5 Proportions of peptides in the 3 CV groups (< 10% in dark red, between 10 and 15% in light red, and ≥ 15% in grey) with LIT and OT mass analyzer at different scanning speeds (Turbo, Rapid, Normal), resolution (7000, 15000 and 3000) and inputs (1-, 5-, 10-, 100 ng).


# Load packages

```{r, message = FALSE}
library("tidyverse")
library("patchwork")

#set bw theme as default theme
theme_set(theme_bw())
```

# Load data

The path to every folder is stored to keep everything compact. LIT data is stored in the folder located in lit_path and OT data in ot_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
ot_path  <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/OT/"
```

```{r}
#lit_path <- "C:/Data/LIT/"
#ot_path <- "C:/Data/OT/"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606)
in csv files and need to be loaded in R with the function `read.csv2()`.

LIT Turbo DIA

```{r}
LITDIA_Turbo_1 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_100 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

LIT Rapid DIA

```{r}
LITDIA_Rapid_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

LIT Normal DIA

```{r}
LITDIA_Normal_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

OT 7.5k DIA

```{r}
OTDIA_7k_1 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_5 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_10 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_100 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

OT 15k DIA

```{r}
OTDIA_15k_1 <- read.csv2(paste0(ot_path, "20220421_OT_15k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_5 <- read.csv2(paste0(ot_path, "20220509_OT_15k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_10 <- read.csv2(paste0(ot_path, "20220502_OT_15k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_100 <- read.csv2(paste0(ot_path, "20220425_OT_15k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

OT 30k DIA

```{r}
OTDIA_30k_1 <- read.csv2(paste0(ot_path, "20220421_OT_30k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_5 <- read.csv2(paste0(ot_path, "20220509_OT_30k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_10 <- read.csv2(paste0(ot_path, "20220502_OT_30k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_100 <- read.csv2(paste0(ot_path, "20220425_OT_30k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

# Clean data tables

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It also calculates the mean between the four replicates. Spectronaut does some imputation by default, but we want to keep missing values. Imputed values are replaced by NA. Peptides missing in more than one replicate are highlighted as TRUE.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  mutate(na_nbr = rowSums(is.na(y[-1]))) %>%
  mutate(mean_quantity = rowMeans(y[2:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("
Highlighted ", sum(z$filtered) , " peptide(s) found in less than ", ncol(y) -2, " replicates")
  
  return(z)
}
```

The `filter_pep()` function is used for every data-set. Furthermore a “filter” data-set is created by removing all peptides missing in more than one replicate.

1 ng

```{r}
OTDIA_7k_1 <-  filter_pep(OTDIA_7k_1)
OTDIA_7k_1_filter <- OTDIA_7k_1[OTDIA_7k_1$filtered == FALSE,]

OTDIA_15k_1 <-  filter_pep(OTDIA_15k_1)
OTDIA_15k_1_filter <- OTDIA_15k_1[OTDIA_15k_1$filtered == FALSE,]

OTDIA_30k_1 <-  filter_pep(OTDIA_30k_1)
OTDIA_30k_1_filter <- OTDIA_30k_1[OTDIA_30k_1$filtered == FALSE,]

LITDIA_Turbo_1 <- filter_pep(LITDIA_Turbo_1)
LITDIA_Turbo_1_filter <- LITDIA_Turbo_1[LITDIA_Turbo_1$filtered == FALSE,]

LITDIA_Rapid_1 <- filter_pep(LITDIA_Rapid_1)
LITDIA_Rapid_1_filter <- LITDIA_Rapid_1[LITDIA_Rapid_1$filtered == FALSE,]

LITDIA_Normal_1 <- filter_pep(LITDIA_Normal_1)
LITDIA_Normal_1_filter <- LITDIA_Normal_1[LITDIA_Normal_1$filtered == FALSE,]
```

5 ng

```{r}
OTDIA_7k_5 <-  filter_pep(OTDIA_7k_5)
OTDIA_7k_5_filter <- OTDIA_7k_5[OTDIA_7k_5$filtered == FALSE,]

OTDIA_15k_5 <-  filter_pep(OTDIA_15k_5)
OTDIA_15k_5_filter <- OTDIA_15k_5[OTDIA_15k_5$filtered == FALSE,]

OTDIA_30k_5 <-  filter_pep(OTDIA_30k_5)
OTDIA_30k_5_filter <- OTDIA_30k_5[OTDIA_30k_5$filtered == FALSE,]

LITDIA_Turbo_5 <- filter_pep(LITDIA_Turbo_5)
LITDIA_Turbo_5_filter <- LITDIA_Turbo_5[LITDIA_Turbo_5$filtered == FALSE,]

LITDIA_Rapid_5 <- filter_pep(LITDIA_Rapid_5)
LITDIA_Rapid_5_filter <- LITDIA_Rapid_5[LITDIA_Rapid_5$filtered == FALSE,]

LITDIA_Normal_5 <- filter_pep(LITDIA_Normal_5)
LITDIA_Normal_5_filter <- LITDIA_Normal_5[LITDIA_Normal_5$filtered == FALSE,]
```

10 ng

```{r}
OTDIA_7k_10 <-  filter_pep(OTDIA_7k_10)
OTDIA_7k_10_filter <- OTDIA_7k_10[OTDIA_7k_10$filtered == FALSE,]

OTDIA_15k_10 <-  filter_pep(OTDIA_15k_10)
OTDIA_15k_10_filter <- OTDIA_15k_10[OTDIA_15k_10$filtered == FALSE,]

OTDIA_30k_10 <-  filter_pep(OTDIA_30k_10)
OTDIA_30k_10_filter <- OTDIA_30k_10[OTDIA_30k_10$filtered == FALSE,]

LITDIA_Turbo_10 <- filter_pep(LITDIA_Turbo_10)
LITDIA_Turbo_10_filter <- LITDIA_Turbo_10[LITDIA_Turbo_10$filtered == FALSE,]

LITDIA_Rapid_10 <- filter_pep(LITDIA_Rapid_10)
LITDIA_Rapid_10_filter <- LITDIA_Rapid_10[LITDIA_Rapid_10$filtered == FALSE,]

LITDIA_Normal_10 <- filter_pep(LITDIA_Normal_10)
LITDIA_Normal_10_filter <- LITDIA_Normal_10[LITDIA_Normal_10$filtered == FALSE,]
```

100 ng

```{r}
OTDIA_7k_100 <-  filter_pep(OTDIA_7k_100)
OTDIA_7k_100_filter <- OTDIA_7k_100[OTDIA_7k_100$filtered == FALSE,]

OTDIA_15k_100 <-  filter_pep(OTDIA_15k_100)
OTDIA_15k_100_filter <- OTDIA_15k_100[OTDIA_15k_100$filtered == FALSE,]

OTDIA_30k_100 <-  filter_pep(OTDIA_30k_100)
OTDIA_30k_100_filter <- OTDIA_30k_100[OTDIA_30k_100$filtered == FALSE,]

LITDIA_Turbo_100 <- filter_pep(LITDIA_Turbo_100)
LITDIA_Turbo_100_filter <- LITDIA_Turbo_100[LITDIA_Turbo_100$filtered == FALSE,]

LITDIA_Rapid_100 <- filter_pep(LITDIA_Rapid_100)
LITDIA_Rapid_100_filter <- LITDIA_Rapid_100[LITDIA_Rapid_100$filtered == FALSE,]

LITDIA_Normal_100 <- filter_pep(LITDIA_Normal_100)
LITDIA_Normal_100_filter <- LITDIA_Normal_100[LITDIA_Normal_100$filtered == FALSE,]
```


# Compute CV

The function `compute_CV()` below takes the data-sets, already filtered by `filter_pep()`, as an entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our data-sets include four replicates but some contain only three. In this case, an empty column is added as a fourth replicate to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the method and the input are included afterwards.

### 1 ng

LIT

```{r}
LITDIA_Turbo_1_CV <- compute_CV(LITDIA_Turbo_1)
LITDIA_Turbo_1_CV$method <- "Turbo"
LITDIA_Turbo_1_CV$input<- 1
LITDIA_Rapid_1_CV <- compute_CV(LITDIA_Rapid_1)
LITDIA_Rapid_1_CV$method <- "Rapid"
LITDIA_Rapid_1_CV$input<- 1
LITDIA_Normal_1_CV <- compute_CV(LITDIA_Normal_1)
LITDIA_Normal_1_CV$method <- "Normal"
LITDIA_Normal_1_CV$input<- 1
```

OT

```{r}
OTDIA_7k_1_CV <- compute_CV(OTDIA_7k_1)
OTDIA_7k_1_CV$method <- "7k"
OTDIA_7k_1_CV$input<- 1
OTDIA_15k_1_CV <- compute_CV(OTDIA_15k_1)
OTDIA_15k_1_CV$method <- "15k"
OTDIA_15k_1_CV$input<- 1
OTDIA_30k_1_CV <- compute_CV(OTDIA_30k_1)
OTDIA_30k_1_CV$method <- "30k"
OTDIA_30k_1_CV$input<- 1
```

### 5 ng

LIT

```{r}
LITDIA_Turbo_5_CV <- compute_CV(LITDIA_Turbo_5)
LITDIA_Turbo_5_CV$method <- "Turbo"
LITDIA_Turbo_5_CV$input<- 5
LITDIA_Rapid_5_CV <- compute_CV(LITDIA_Rapid_5)
LITDIA_Rapid_5_CV$method <- "Rapid"
LITDIA_Rapid_5_CV$input<- 5
LITDIA_Normal_5_CV <- compute_CV(LITDIA_Normal_5)
LITDIA_Normal_5_CV$method <- "Normal"
LITDIA_Normal_5_CV$input<- 5
```

OT

```{r}
OTDIA_7k_5_CV <- compute_CV(OTDIA_7k_5)
OTDIA_7k_5_CV$method <- "7k"
OTDIA_7k_5_CV$input<- 5
OTDIA_15k_5_CV <- compute_CV(OTDIA_15k_5)
OTDIA_15k_5_CV$method <- "15k"
OTDIA_15k_5_CV$input<- 5
OTDIA_30k_5_CV <- compute_CV(OTDIA_30k_5)
OTDIA_30k_5_CV$method <- "30k"
OTDIA_30k_5_CV$input<- 5
```

### 10 ng

LIT

```{r}
LITDIA_Turbo_10_CV <- compute_CV(LITDIA_Turbo_10)
LITDIA_Turbo_10_CV$method <- "Turbo"
LITDIA_Turbo_10_CV$input<- 10
LITDIA_Rapid_10_CV <- compute_CV(LITDIA_Rapid_10)
LITDIA_Rapid_10_CV$method <- "Rapid"
LITDIA_Rapid_10_CV$input<- 10
LITDIA_Normal_10_CV <- compute_CV(LITDIA_Normal_10)
LITDIA_Normal_10_CV$method <- "Normal"
LITDIA_Normal_10_CV$input<- 10
```

OT

```{r}
OTDIA_7k_10_CV <- compute_CV(OTDIA_7k_10)
OTDIA_7k_10_CV$method <- "7k"
OTDIA_7k_10_CV$input<- 10
OTDIA_15k_10_CV <- compute_CV(OTDIA_15k_10)
OTDIA_15k_10_CV$method <- "15k"
OTDIA_15k_10_CV$input<- 10
OTDIA_30k_10_CV <- compute_CV(OTDIA_30k_10)
OTDIA_30k_10_CV$method <- "30k"
OTDIA_30k_10_CV$input<- 10
```

### 100 ng

LIT

```{r}
LITDIA_Turbo_100_CV <- compute_CV(LITDIA_Turbo_100)
LITDIA_Turbo_100_CV$method <- "Turbo"
LITDIA_Turbo_100_CV$input<- 100
LITDIA_Rapid_100_CV <- compute_CV(LITDIA_Rapid_100)
LITDIA_Rapid_100_CV$method <- "Rapid"
LITDIA_Rapid_100_CV$input<- 100
LITDIA_Normal_100_CV <- compute_CV(LITDIA_Normal_100)
LITDIA_Normal_100_CV$method <- "Normal"
LITDIA_Normal_100_CV$input<- 100
```

OT

```{r}
OTDIA_7k_100_CV <- compute_CV(OTDIA_7k_100)
OTDIA_7k_100_CV$method <- "7k"
OTDIA_7k_100_CV$input<- 100
OTDIA_15k_100_CV <- compute_CV(OTDIA_15k_100)
OTDIA_15k_100_CV$method <- "15k"
OTDIA_15k_100_CV$input<- 100
OTDIA_30k_100_CV <- compute_CV(OTDIA_30k_100)
OTDIA_30k_100_CV$method <- "30k"
OTDIA_30k_100_CV$input<- 100
```

# Join

Data frames containing CV are combined using `rbind()`.

```{r}
CV_LIT <- 
  rbind(LITDIA_Turbo_1_CV, LITDIA_Rapid_1_CV, LITDIA_Normal_1_CV,
      LITDIA_Turbo_5_CV, LITDIA_Rapid_5_CV, LITDIA_Normal_5_CV,
      LITDIA_Turbo_10_CV, LITDIA_Rapid_10_CV, LITDIA_Normal_10_CV,
      LITDIA_Turbo_100_CV, LITDIA_Rapid_100_CV, LITDIA_Normal_100_CV)

CV_LIT$mass_analyzer <- "LIT"

CV_OT <- 
  rbind(OTDIA_7k_1_CV, OTDIA_15k_1_CV, OTDIA_30k_1_CV,
      OTDIA_7k_5_CV, OTDIA_15k_5_CV, OTDIA_30k_5_CV,
      OTDIA_7k_10_CV, OTDIA_15k_10_CV, OTDIA_30k_10_CV,
      OTDIA_7k_100_CV, OTDIA_15k_100_CV, OTDIA_30k_100_CV)

CV_OT$mass_analyzer <- "OT"

CV_joined <- rbind(CV_LIT, CV_OT)


CV_joined$method %>% table()
CV_joined$input %>% table()

# Factorise to set order
CV_joined$method <- factor(CV_joined$method, 
                          levels = unique(CV_joined$method))
CV_joined$input <- factor(CV_joined$input, 
                          levels = unique(CV_joined$input))
```

A new column called “CV_filter” is added to identify peptides with a CV
over 0.15 (1), between 0.1 and 0.15 (2) and under 0.1 (3).

```{r}
CV_joined$CV_filter <- NA
CV_joined$CV_filter[CV_joined$CV < 0.1] <- "3"
CV_joined$CV_filter[CV_joined$CV >= 0.1 & CV_joined$CV <= 0.15] <- "2"
CV_joined$CV_filter[CV_joined$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out. The number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method. The proportion represented by each CV is calculated by dividing the number of peptides in a specific group by the total number of peptides.

```{r}
CV_joined <- CV_joined %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(method, mass_analyzer, input, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))
CV_joined$mean_id <- rowMeans(CV_joined[5:8], na.rm = TRUE)
CV_joined$sd_id <- apply(CV_joined[5:8], FUN =  sd, MARGIN = 1, na.rm = TRUE)

CV_tot <- CV_joined %>% 
  group_by(method, input) %>% 
  summarise(id_tot_1 = sum(id_S1),
            id_tot_2 = sum(id_S2),
            id_tot_3 = sum(id_S3),
            id_tot_4 = sum(id_S4))

tot_S1 <- tot_S2 <- tot_S3 <- tot_S4 <- rep(NA, 72)

for(i in c(1:72)){
  tot_S1[i] <- CV_tot$id_tot_1[ceiling(i/3)]}

for(i in c(1:72)){
  tot_S2[i] <- CV_tot$id_tot_2[ceiling(i/3)]}

for(i in c(1:72)){
  tot_S3[i] <- CV_tot$id_tot_3[ceiling(i/3)]}

for(i in c(1:72)){
  tot_S4[i] <- CV_tot$id_tot_4[ceiling(i/3)]}
CV_tot$id_tot_1[1]

CV_prop <- CV_joined %>% 
  as.data.frame() %>% 
  mutate(CV_proportion_S1 = (id_S1/tot_S1)*100,
         CV_proportion_S2 = (id_S2/tot_S2)*100,
         CV_proportion_S3 = (id_S3/tot_S3)*100,
         CV_proportion_S4 = (id_S4/tot_S4)*100)

CV_prop$mean_id_prop <- rowMeans(CV_prop[11:14], na.rm = TRUE)
CV_prop$sd_id_prop <- apply(CV_prop[11:14], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

# Plot

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot2`. Error bars representing the standard deviation are displayed using `geom_errorbar()`. Due to the “stacked” aspect of the col plot, error bars y position is adjusted by using the y_errorbar variable instead of the mean_id.

```{r}
CV_prop$y_errorbar <- CV_prop$mean_id_prop
CV_prop$y_errorbar[CV_prop$CV_filter == "1"] <- 
  CV_prop$y_errorbar[CV_prop$CV_filter == "1"] +
  CV_prop$y_errorbar[CV_prop$CV_filter == "2"]+
  CV_prop$y_errorbar[CV_prop$CV_filter == "3"]
CV_prop$y_errorbar[CV_prop$CV_filter == "2"] <-
  CV_prop$y_errorbar[CV_prop$CV_filter == "2"]+
  CV_prop$y_errorbar[CV_prop$CV_filter == "3"]

CV_prop_LIT <- CV_prop %>% 
  filter(method %in% c("Turbo", "Rapid", "Normal")) %>% 
  ggplot(aes(x = input, y = mean_id_prop, fill = CV_filter)) +
  geom_col(width = 0.7) +
  facet_grid(mass_analyzer ~ method) +
  labs(x = "Input (ng)",
       y = "Peptide proportion (%)",
       fill = "CV") +
  geom_errorbar(aes(ymin = y_errorbar - sd_id_prop,
                    ymax = y_errorbar + sd_id_prop),
                width = 0.2,
                size = 1) +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        plot.margin = margin(l = 25),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        legend.key.size = unit(0.9, "cm"),
        legend.position = "top",
        axis.ticks.x = element_blank())+
  scale_y_continuous(limits = c(0, 108),
                     breaks = c(0, 25, 50, 75, 100))+
  scale_fill_manual(values = c("grey82", "#ffaa8b", "#ff713e"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))

CV_prop_OT <- CV_prop %>% 
  filter(method %in% c("7k", "15k", "30k")) %>% 
  ggplot(aes(x = input, y = mean_id_prop, fill = CV_filter))+
  geom_col(width = 0.7) +
  facet_grid(mass_analyzer ~ method) +
  labs(x = "Input (ng)",
       y = "Peptide proportion (%)",
       fill = "CV") +
  geom_errorbar(aes(ymin = y_errorbar - sd_id_prop,
                    ymax = y_errorbar + sd_id_prop),
                width = 0.2,
                size = 1) +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2,
                                    hjust = 12),
        plot.margin = margin(l = 25),
        legend.position = "none")+
  scale_y_continuous(limits = c(0, 108),
                     breaks = c(0, 25, 50, 75, 100))+
  scale_fill_manual(values = c("grey82", "#ffaa8b", "#ff713e"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))

fig_sup5 <- CV_prop_LIT / CV_prop_OT

#save as pdf
#cairo_pdf(filename = "fig_sup5.pdf", width = 16.67, height = 10.42)
#fig_sup5
#dev.off()
```

