---
title: "Figure 2. Comparison of quantitative reproducibility and accuracy between an Orbitrap Mass Analyser and Linear Ion Trap Mass Analyser on low-input proteomics."
author: "Samuel Grégoire"
output:
  rmarkdown::github_document
---

Figure 2. Comparison of quantitative reproducibility and accuracy between an Orbitrap Mass Analyser and Linear Ion Trap Mass Analyser on low-input proteomics.

# Load packages
```{r, message = FALSE}
library("tidyverse")
library("patchwork")
library("ggpointdensity")
library("ggpubr")

#set bw theme as default theme
theme_set(theme_bw())
```

# Load data

The path to data folders is stored to keep everything compact.
LIT data is stored in the folder located in lit_path and OT data in ot_path.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
ot_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/OT/"
```

```{r}
#lit_path <-"C:/Data/LIT/"
#ot_path <-"C:/Data/OT/"
```

Data tables were exported from Spectronaut in csv files and need to be loaded in R.

## LIT

```{r}
#Turbo
LITDIA_Turbo_1 <- read.csv2(paste0(lit_path, "20220926_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_5 <- read.csv2(paste0(lit_path, "20220926_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_10 <- read.csv2(paste0(lit_path, "20220926_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_100 <- read.csv2(paste0(lit_path, "20220926_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

#Rapid
LITDIA_Rapid_1 <- read.csv2(paste0(lit_path, "20220926_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_5 <- read.csv2(paste0(lit_path, "20220926_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_10 <- read.csv2(paste0(lit_path, "20220926_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_100 <- read.csv2(paste0(lit_path, "20220926_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

#Normal
LITDIA_Normal_1 <- read.csv2(paste0(lit_path, "20220926_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_5 <- read.csv2(paste0(lit_path, "20220926_LIT_Normal_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_10 <- read.csv2(paste0(lit_path, "20220926_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_100 <- read.csv2(paste0(lit_path, "20220926_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

## OT
```{r}
#7.5k
OTDIA_7k_1 <- read.csv2(paste0(ot_path, "20220926_OT_7k_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_7k_5 <- read.csv2(paste0(ot_path, "20220926_OT_7k_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_7k_10 <- read.csv2(paste0(ot_path, "20220926_OT_7k_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_7k_100 <- read.csv2(paste0(ot_path, "20220926_OT_7k_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

#15k
OTDIA_15k_1 <- read.csv2(paste0(ot_path, "20220926_OT_15k_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_15k_5 <- read.csv2(paste0(ot_path, "20220926_OT_15k_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_15k_10 <- read.csv2(paste0(ot_path, "20220926_OT_15k_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_15k_100 <- read.csv2(paste0(ot_path, "20220926_OT_15k_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))

#30k
OTDIA_30k_1 <- read.csv2(paste0(ot_path, "20220926_OT_30k_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_30k_5 <- read.csv2(paste0(ot_path, "20220926_OT_30k_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_30k_10 <- read.csv2(paste0(ot_path, "20220926_OT_30k_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
OTDIA_30k_100 <- read.csv2(paste0(ot_path, "20220926_OT_30k_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

# Clean data tables

Imported tables contain a lot of informations which are not usefull for our analysis. The fonction below performs 5 main steps:
- Create a consensus_PG column containing the same Protein Group for a given peptide. The same peptide sequence can sometime be attributed to a slightly different Protein Group between samples. Since we will not focus on proteoforms, we keep the most used Protein Group for the same peptide sequence as a consensus.
- Replace imputed values by NA (missing values).
- Keep only columns with the file names (replicates), quantitatives values for each file name, the petide sequence and the consensus PG.
- Calculate the mean quantification between replicates.
- Filter out peptides missing in more than 1 replicate.

```{r}
filter_pep <- function(x) {
  x_consensus  <- x %>% 
    group_by(PEP.StrippedSequence) %>% 
    mutate(consensus_PG = names(sort(table(PG.ProteinGroups),
                                     decreasing = TRUE))[1])
  x_consensus$F.PeakHeight[as.logical(x_consensus $EG.IsImputed)] <- NA
  x_clean_with_mean  <- x_consensus  %>% 
  group_by(R.Replicate, PEP.StrippedSequence, consensus_PG) %>% 
  summarise(mean_peakh = mean(F.PeakHeight, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.Replicate, 
              values_from = mean_peakh) %>%
    suppressMessages()
  x_filter_highlight <- x_clean_with_mean  %>% 
  as.data.frame() %>% 
  mutate(na_nbr = rowSums(is.na(x_clean_with_mean [-c(1,2)]))) %>%
  mutate(mean_peakh = 
           rowMeans(x_clean_with_mean[3:ncol(x_clean_with_mean )], 
                    na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr)  %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("Filtered ", sum(x_filter_highlight$filtered), " peptide(s) found in less than ", ncol(x_clean_with_mean ) -3, " replicates")
  x_filtered  <- x_filter_highlight %>% 
  filter(filtered == FALSE)
 return(x_filtered) }
```


The filter_pep function is run on every dataset. Informations about inputs and methods are added.

## LIT

```{r}
#Turbo
LITDIA_Turbo_1_filter <- 
  filter_pep(LITDIA_Turbo_1)
LITDIA_Turbo_1_filter$input <- 1
LITDIA_Turbo_1_filter$method <- "Turbo"

LITDIA_Turbo_5_filter <- 
  filter_pep(LITDIA_Turbo_5)
LITDIA_Turbo_5_filter$input <- 5
LITDIA_Turbo_5_filter$method <- "Turbo"

LITDIA_Turbo_10_filter <- 
  filter_pep(LITDIA_Turbo_10)
LITDIA_Turbo_10_filter$input <- 10
LITDIA_Turbo_10_filter$method <- "Turbo"

LITDIA_Turbo_100_filter <- 
  filter_pep(LITDIA_Turbo_100)
LITDIA_Turbo_100_filter$input <- 100
LITDIA_Turbo_100_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_1_filter <- 
  filter_pep(LITDIA_Rapid_1)
LITDIA_Rapid_1_filter$input <- 1
LITDIA_Rapid_1_filter$method <- "Rapid"

LITDIA_Rapid_5_filter <- 
  filter_pep(LITDIA_Rapid_5)
LITDIA_Rapid_5_filter$input <- 5
LITDIA_Rapid_5_filter$method <- "Rapid"

LITDIA_Rapid_10_filter <- 
  filter_pep(LITDIA_Rapid_10)
LITDIA_Rapid_10_filter$input <- 10
LITDIA_Rapid_10_filter$method <- "Rapid"

LITDIA_Rapid_100_filter <- 
  filter_pep(LITDIA_Rapid_100)
LITDIA_Rapid_100_filter$input <- 100
LITDIA_Rapid_100_filter$method <- "Rapid"

#Normal
LITDIA_Normal_1_filter <- 
  filter_pep(LITDIA_Normal_1)
LITDIA_Normal_1_filter$input <- 1
LITDIA_Normal_1_filter$method <- "Normal"

LITDIA_Normal_5_filter <- 
  filter_pep(LITDIA_Normal_5)
LITDIA_Normal_5_filter$input <- 5
LITDIA_Normal_5_filter$method <- "Normal"

LITDIA_Normal_10_filter <- 
  filter_pep(LITDIA_Normal_10)
LITDIA_Normal_10_filter$input <- 10
LITDIA_Normal_10_filter$method <- "Normal"

LITDIA_Normal_100_filter <- 
  filter_pep(LITDIA_Normal_100)
LITDIA_Normal_100_filter$input <- 100
LITDIA_Normal_100_filter$method <- "Normal"
```

## OT

```{r}
#7.5k
OTDIA_7k_1_filter <- 
  filter_pep(OTDIA_7k_1)
OTDIA_7k_1_filter$input <- 1
OTDIA_7k_1_filter$method <- "7.5k"

OTDIA_7k_5_filter <- 
  filter_pep(OTDIA_7k_5)
OTDIA_7k_5_filter$input <- 5
OTDIA_7k_5_filter$method <- "7.5k"

OTDIA_7k_10_filter <- 
  filter_pep(OTDIA_7k_10)
OTDIA_7k_10_filter$input <- 10
OTDIA_7k_10_filter$method <- "7.5k"

OTDIA_7k_100_filter <- 
  filter_pep(OTDIA_7k_100)
OTDIA_7k_100_filter$input <- 100
OTDIA_7k_100_filter$method <- "7.5k"

#15k
OTDIA_15k_1_filter <- 
  filter_pep(OTDIA_15k_1)
OTDIA_15k_1_filter$input <- 1
OTDIA_15k_1_filter$method <- "15k"

OTDIA_15k_5_filter <- 
  filter_pep(OTDIA_15k_5)
OTDIA_15k_5_filter$input <- 5
OTDIA_15k_5_filter$method <- "15k"

OTDIA_15k_10_filter <- 
  filter_pep(OTDIA_15k_10)
OTDIA_15k_10_filter$input <- 10
OTDIA_15k_10_filter$method <- "15k"

OTDIA_15k_100_filter <- 
  filter_pep(OTDIA_15k_100)
OTDIA_15k_100_filter$input <- 100
OTDIA_15k_100_filter$method <- "15k"

#30k
OTDIA_30k_1_filter <- 
  filter_pep(OTDIA_30k_1)
OTDIA_30k_1_filter$input <- 1
OTDIA_30k_1_filter$method <- "30k"

OTDIA_30k_5_filter <- 
  filter_pep(OTDIA_30k_5)
OTDIA_30k_5_filter$input <- 5
OTDIA_30k_5_filter$method <- "30k"

OTDIA_30k_10_filter <- 
  filter_pep(OTDIA_30k_10)
OTDIA_30k_10_filter$input <- 10
OTDIA_30k_10_filter$method <- "30k"

OTDIA_30k_100_filter <- 
  filter_pep(OTDIA_30k_100)
OTDIA_30k_100_filter$input <- 100
OTDIA_30k_100_filter$method <- "30k"
```

# Join datasets

LIT and OT datasets are joined and a column mass_analyzer is added.

```{r}
LIT <- rbind(LITDIA_Turbo_1_filter,
      LITDIA_Turbo_5_filter, 
      LITDIA_Turbo_10_filter,
      LITDIA_Turbo_100_filter,
      LITDIA_Rapid_1_filter,
      LITDIA_Rapid_5_filter,
      LITDIA_Rapid_10_filter,
      LITDIA_Rapid_100_filter,
      LITDIA_Normal_1_filter,
      LITDIA_Normal_5_filter,
      LITDIA_Normal_10_filter,
      LITDIA_Normal_100_filter)
LIT$mass_analyzer <- "LIT"

OT <- rbind(OTDIA_7k_1_filter,
      OTDIA_7k_5_filter, 
      OTDIA_7k_10_filter,
      OTDIA_7k_100_filter,
      OTDIA_15k_1_filter,
      OTDIA_15k_5_filter,
      OTDIA_15k_10_filter,
      OTDIA_15k_100_filter,
      OTDIA_30k_1_filter,
      OTDIA_30k_5_filter,
      OTDIA_30k_10_filter,
      OTDIA_30k_100_filter)
OT$mass_analyzer <- "OT"

LITvsOT <- rbind(LIT, OT)

#clean colnames
colnames(LITvsOT)[3:6] <- paste("Replicate", colnames(LITvsOT)[3:6], sep = "_")

#factor method
LITvsOT$method <- 
  factor(LITvsOT$method, 
         levels = c("7.5k", "15k", "30k", "Turbo", "Rapid", "Normal"))
```

# Figure A

## Peptide aggregation

To infer the protein intensities from peptides, we aggregated peptides using for each replicate the mean of each peptides belonging to the same Protein Group.

```{r}
dim(LITvsOT)
LITvsOT_prot <- LITvsOT %>%
  group_by(consensus_PG, mass_analyzer, input, method) %>% 
  summarise(prot_1 = mean(Replicate_1),
            prot_2 = mean(Replicate_2),
            prot_3 = mean(Replicate_3),
            prot_4 = mean(Replicate_4))
dim(LITvsOT_prot)

LITvsOT_prot %>% 
  ggplot(aes(y = log10(prot_1)))+
  geom_boxplot()+
  geom_hline(yintercept = 0,
             color = "red",
             linetype = "dashed")

LITvsOT_prot %>% 
  ggplot(aes(y = log10(prot_2)))+
  geom_boxplot()+
  geom_hline(yintercept = log10(5),
             color = "red",
             linetype = "dashed")

LITvsOT_prot <- LITvsOT_prot %>% 
  filter(prot_1 > 5 &
           prot_2 > 5)

```

## Plot A

Correlations bewteen replicate one and replicate two are plotted for each method and input in scatter plots using ggplot.

```{r}
#Calculate limits for each axis
lim_x <- 
  log10(c(min(LITvsOT_prot$prot_1[LITvsOT_prot$prot_1 != 1], na.rm = TRUE), 
    max(LITvsOT_prot$prot_1, na.rm = TRUE)))
lim_y <- 
 log10(c(min(LITvsOT_prot$prot_2[LITvsOT_prot$prot_2 != 1], na.rm = TRUE),
    max(LITvsOT_prot$prot_2, na.rm = TRUE)))

# 1 ng
corr_prot_1ng_LIT <- LITvsOT_prot %>% 
  filter(input == 1 &
           mass_analyzer == "LIT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "A                               1 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = -0.32,
                                  vjust = 3,
                                  face = "bold"))

corr_prot_1ng_OT <- LITvsOT_prot %>% 
  filter(input == 1 &
           mass_analyzer == "OT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "1 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"))

# 5 ng
corr_prot_5ng_LIT <- LITvsOT_prot %>% 
  filter(input == 5 &
           mass_analyzer == "LIT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "5 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"))

corr_prot_5ng_OT <- LITvsOT_prot %>% 
  filter(input == 5 &
           mass_analyzer == "OT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "5 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"))

# 10 ng
corr_prot_10ng_LIT <- LITvsOT_prot %>% 
  filter(input == 10 &
           mass_analyzer == "LIT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "10 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"))


corr_prot_10ng_OT <- LITvsOT_prot %>% 
  filter(input == 10 &
           mass_analyzer == "OT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "10 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"),
        plot.margin = margin(b = 20))


# 100 ng
corr_prot_100ng_LIT <- LITvsOT_prot %>% 
  filter(input == 100 &
           mass_analyzer == "LIT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "100 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"))

corr_prot_100ng_OT <- LITvsOT_prot %>% 
  filter(input == 100 &
           mass_analyzer == "OT") %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(mass_analyzer ~ method)+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(title = "100 ng input",
       x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 29,
                                  hjust = 0.5,
                                  vjust = 3,
                                  face = "bold"),
        plot.margin = margin(b = 20))
```

Plots from 1, 5, 10 and 100 ng are joined using patchwork.

```{r}
# 1 ng
corr_1ng_prot <- 
  (corr_prot_1ng_LIT+
     theme(axis.title = element_blank(),
           axis.text.x = element_blank(),
           axis.ticks.x = element_blank()))/
  (corr_prot_1ng_OT+
     theme(axis.title.x = element_blank(),
           axis.title.y = element_text(hjust = -0.15, vjust = 2.5),
           plot.title = element_blank(),
           plot.margin = margin(b = 22)))

# 5 ng
corr_5ng_prot <- (corr_prot_5ng_LIT +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()))/
  (corr_prot_5ng_OT +
     theme(axis.title = element_blank(),
           axis.title.y = element_blank(),
           plot.title = element_blank(),
           plot.margin = margin(b = 22)))

# 10 ng
corr_10ng_prot <- (corr_prot_10ng_LIT +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          plot.margin = margin(t = 22)))/
  (corr_prot_10ng_OT +
     theme(axis.title.y = element_text(hjust = -0.15, vjust = 2.5),
           plot.title = element_blank(),
           axis.title.x = element_text(vjust = -0.7)))

# 100 ng
corr_100ng_prot <- (corr_prot_100ng_LIT +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          plot.margin = margin(t = 22)))/
  (corr_prot_100ng_OT +
     theme(axis.title.y = element_blank(),
           plot.title = element_blank(),
           axis.title.x = element_text(vjust = -0.7)))

figure2a <- wrap_plots(corr_1ng_prot, corr_5ng_prot, 
                       corr_10ng_prot, corr_100ng_prot, 
                       ncol = 2, nrow = 2)
```

# Figure S6

```{r}
LITvsOT_prot$method <- factor(LITvsOT_prot$method, levels = c("Turbo", "Rapid", "Normal", "7.5k", "15k", "30k"))

fig_S6 <- LITvsOT_prot %>% 
  filter(input %in% c(1, 100) &
          method %in% c("Normal", "30k")) %>%  
  ggplot(aes(x = log10(prot_1), y = log10(prot_2)))+
  geom_pointdensity(size = 1.5)+
  scale_color_viridis_c()+
  facet_grid(input ~ method, 
             labeller = as_labeller(c('1' = "1 ng",
                                      '100' = "100 ng",
                                      "Normal" = "LIT Normal",
                                      "30k" = "OT 30k")))+
  scale_x_continuous(limits = lim_x)+
  scale_y_continuous(limits = lim_y)+
  theme_bw()+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3,
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(x = "log10(F.PeakHeight) Replicate #1",
       y = "log10(F.PeakHeight) Replicate #2")+
  theme(legend.position = "none",
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.margin = margin(b = 20))

fig_S6

#cairo_pdf(filename = "fig_sup6.pdf", width = 10.42, height = 8.33)
#fig_S6
#dev.off()
```

# Figure B

The linear quantitative response curve on peptide level of the dilution series of tryptic HeLa (1-, 5-, 10-, and 100 ng).

## Normalise intensity

To help interpretability, intensity from different methods are normalised to make the median value of 1 ng represent an intensity of 1. The is acheived by dividing all intensities by the median value of the 1 ng sample of the corresponding method.

```{r}
LITvsOT_wide <- LITvsOT[, -c(3:6, 8)] %>% 
  pivot_wider(names_from = method, values_from = mean_peakh)
  
LITvsOT_wide_norm <- LITvsOT_wide %>% 
  mutate(Turbo_normalised = 
           Turbo/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$Turbo, 
                                         na.rm = TRUE)) %>% 
  mutate(Rapid_normalised = 
           Rapid/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$Rapid, 
                                         na.rm = TRUE)) %>% 
  mutate(Normal_normalised = 
           Turbo/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$Normal,
                                          na.rm = TRUE)) %>% 
  mutate(`7.5k_normalised` = 
           `7.5k`/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$`7.5k`,
                                           na.rm = TRUE)) %>% 
  mutate(`15k_normalised` = 
           `15k`/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$`15k`,
                                           na.rm = TRUE)) %>% 
  mutate(`30k_normalised` = 
           `30k`/median(LITvsOT_wide[LITvsOT_wide$input == 1,]$`30k`,
                                           na.rm = TRUE))

LITvsOT_norm <- LITvsOT_wide_norm[, -c(5:10)] %>%
  pivot_longer(names_to = "method", 
               values_to = "normalised_intensity",
               -c(PEP.StrippedSequence, consensus_PG,
                  input, mass_analyzer)) %>% 
  filter(!is.na(normalised_intensity))

#factor method
LITvsOT_norm$method <- 
  factor(LITvsOT_norm$method, 
         levels = c("7.5k_normalised", "15k_normalised", 
                    "30k_normalised", "Turbo_normalised",
                    "Rapid_normalised", "Normal_normalised"))
```

## Plot B

Distributions of intensities are plotted for each methods and input in boxplots using ggplot. Outliers are not shown.

```{r}
intensity_boxplot_LIT <- LITvsOT_norm %>% 
  filter(mass_analyzer == "LIT") %>% 
  ggplot(aes(x = as.factor(input), y = log10(normalised_intensity)))+
  geom_boxplot(outlier.shape = NA,
               fill = "#D1E5EB",
               size = 0.7)+
  scale_y_continuous(limits = c(-1.2, 2.5))+
  facet_grid(mass_analyzer ~ method, 
             labeller = as_labeller(c("Turbo_normalised" = "Turbo",
                                      "Rapid_normalised" = "Rapid",
                                      "Normal_normalised" = "Normal",
                                      "LIT" = "LIT")))+
  theme_bw()+
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.1),
        plot.margin = margin(t = 25))+
  labs(x = "Input (ng)",
       y = "log10(Normalised F.PeakHeight)",
       title = "B")

intensity_boxplot_OT <- LITvsOT_norm %>% 
  filter(mass_analyzer == "OT") %>% 
  ggplot(aes(x = as.factor(input), y = log10(normalised_intensity)))+
  geom_boxplot(outlier.shape = NA,
               fill = "#D1E5EB",
               size = 0.7)+
  scale_y_continuous(limits = c(-1.2, 2.5))+
  facet_grid(mass_analyzer ~ method, 
             labeller = as_labeller(c("7.5k_normalised" = "7.5k",
                                      "15k_normalised" = "15k",
                                      "30k_normalised" = "30k",
                                      "OT" = "OT")))+
  theme_bw()+
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.1))+
  labs(x = "Input (ng)",
       y = "log10(Normalised F.PeakHeight)")
```

Plots from LIT and OT are joined together using patchwork.

```{r}
figure2b <- 
  (intensity_boxplot_LIT  +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()))/
  (intensity_boxplot_OT +
     theme(axis.title.y = element_text(hjust = -0.25, vjust = 2.5)))
figure2b
```

# Join A and B

```{r}
figure2b <- 
  (plot_spacer() + figure2b + plot_spacer()) +
  plot_layout(width = c(0.4, 3, 0.4))

figure2 <- (figure2a / figure2b) + plot_layout(heights = c(2,1))

#Save as pdf
#cairo_pdf(filename = "fig2.pdf", width = 18.75, height = 25)
#figure2
#dev.off()
```
