---
title: "Supporting figure S4 Comparison of the number of identified proteins groups"
author: "Samuel Grégoire"
output:
  rmarkdown::github_document
---

Supporting figure S4 Comparison of the number of identified proteins groups in serial dilution (1, 5, 10, and 100 ng) of HeLa tryptic digested between DIA-OT-based methods with different resolution scans (7.5k, 15k, and 30k) and DIA-LIT-based methods with different scanning modes (Turbo, Rapid, Normal on 40 SPD) by Spectronaut version 15.


# Load packages

```{r, message = FALSE}
library("tidyverse")
```

# Load data

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
ot_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/OT/"
```

```{r}
#lit_path <- "C:/Data/LIT/"
#ot_path <- "C:/Data/OT/"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606) in csv files and need to be loaded in RStudio with the function `read.csv2()`.

## LIT

### Turbo

```{r}
LITDIA_Turbo_1 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_100 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

### Rapid

```{r}
LITDIA_Rapid_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

### Normal

```{r}
LITDIA_Normal_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

## OT

### 7.5k

```{r}
OTDIA_7k_1 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_5 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_10 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_100 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

### 15k

```{r}
OTDIA_15k_1 <- read.csv2(paste0(ot_path, "20220421_OT_15k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_5 <- read.csv2(paste0(ot_path, "20220509_OT_15k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_10 <- read.csv2(paste0(ot_path, "20220502_OT_15k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_100 <- read.csv2(paste0(ot_path, "20220425_OT_15k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

### 30k

```{r}
OTDIA_30k_1 <- read.csv2(paste0(ot_path, "20220421_OT_30k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_5 <- read.csv2(paste0(ot_path, "20220509_OT_30k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_10 <- read.csv2(paste0(ot_path, "20220502_OT_30k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_100 <- read.csv2(paste0(ot_path, "20220425_OT_30k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

# Clean data tables

Imported tables contain a lot of information which is not useful for our analysis. The function below only keep the file names (replicates), quantitatives values for each file name and the peptide sequence. It also calculates the mean between replicates.
Spectronaut does some imputation by default but we want to keep missing values. Imputed values are replaced by NA.
Peptides missing in more than 1 replicates are highlighted (TRUE) in the "filtered" column.

```{r}
filter_pep <- function(w) {
  x <- w %>% 
    group_by(PEP.StrippedSequence) %>% 
    mutate(consensus_PG = names(sort(table(PG.ProteinGroups),
                                     decreasing = TRUE))[1])
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.Replicate, PEP.StrippedSequence, consensus_PG) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.Replicate, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  as.data.frame() %>% 
  mutate(na_nbr = rowSums(is.na(y[-c(1,2)]))) %>%
  mutate(mean_quantity = rowMeans(y[3:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr)  %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("Filtered ", sum(z$filtered), " peptide(s) found in less than ", ncol(y) -3, " replicates")
  t <- z %>% 
  filter(filtered == FALSE)
 return(t) }
```

The filter_pep function is run on every dataset. Informations about inputs and methods are added.

```{r}
#Turbo
LITDIA_Turbo_1_filter <- 
  filter_pep(LITDIA_Turbo_1)
LITDIA_Turbo_1_filter$input <- 1
LITDIA_Turbo_1_filter$method <- "Turbo"

LITDIA_Turbo_5_filter <- 
  filter_pep(LITDIA_Turbo_5)
LITDIA_Turbo_5_filter$input <- 5
LITDIA_Turbo_5_filter$method <- "Turbo"

LITDIA_Turbo_10_filter <- 
  filter_pep(LITDIA_Turbo_10)
LITDIA_Turbo_10_filter$input <- 10
LITDIA_Turbo_10_filter$method <- "Turbo"

LITDIA_Turbo_100_filter <- 
  filter_pep(LITDIA_Turbo_100)
LITDIA_Turbo_100_filter$input <- 100
LITDIA_Turbo_100_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_1_filter <- 
  filter_pep(LITDIA_Rapid_1)
LITDIA_Rapid_1_filter$input <- 1
LITDIA_Rapid_1_filter$method <- "Rapid"

LITDIA_Rapid_5_filter <- 
  filter_pep(LITDIA_Rapid_5)
LITDIA_Rapid_5_filter$input <- 5
LITDIA_Rapid_5_filter$method <- "Rapid"

LITDIA_Rapid_10_filter <- 
  filter_pep(LITDIA_Rapid_10)
LITDIA_Rapid_10_filter$input <- 10
LITDIA_Rapid_10_filter$method <- "Rapid"

LITDIA_Rapid_100_filter <- 
  filter_pep(LITDIA_Rapid_100)
LITDIA_Rapid_100_filter$input <- 100
LITDIA_Rapid_100_filter$method <- "Rapid"

#Normal
LITDIA_Normal_1_filter <- 
  filter_pep(LITDIA_Normal_1)
LITDIA_Normal_1_filter$input <- 1
LITDIA_Normal_1_filter$method <- "Normal"

LITDIA_Normal_5_filter <- 
  filter_pep(LITDIA_Normal_5)
LITDIA_Normal_5_filter$input <- 5
LITDIA_Normal_5_filter$method <- "Normal"

LITDIA_Normal_10_filter <- 
  filter_pep(LITDIA_Normal_10)
LITDIA_Normal_10_filter$input <- 10
LITDIA_Normal_10_filter$method <- "Normal"

LITDIA_Normal_100_filter <- 
  filter_pep(LITDIA_Normal_100)
LITDIA_Normal_100_filter$input <- 100
LITDIA_Normal_100_filter$method <- "Normal"

#7.5k
OTDIA_7k_1_filter <- 
  filter_pep(OTDIA_7k_1)
OTDIA_7k_1_filter$input <- 1
OTDIA_7k_1_filter$method <- "7.5k"

OTDIA_7k_5_filter <- 
  filter_pep(OTDIA_7k_5)
OTDIA_7k_5_filter$input <- 5
OTDIA_7k_5_filter$method <- "7.5k"

OTDIA_7k_10_filter <- 
  filter_pep(OTDIA_7k_10)
OTDIA_7k_10_filter$input <- 10
OTDIA_7k_10_filter$method <- "7.5k"

OTDIA_7k_100_filter <- 
  filter_pep(OTDIA_7k_100)
OTDIA_7k_100_filter$input <- 100
OTDIA_7k_100_filter$method <- "7.5k"

#15k
OTDIA_15k_1_filter <- 
  filter_pep(OTDIA_15k_1)
OTDIA_15k_1_filter$input <- 1
OTDIA_15k_1_filter$method <- "15k"

OTDIA_15k_5_filter <- 
  filter_pep(OTDIA_15k_5)
OTDIA_15k_5_filter$input <- 5
OTDIA_15k_5_filter$method <- "15k"

OTDIA_15k_10_filter <- 
  filter_pep(OTDIA_15k_10)
OTDIA_15k_10_filter$input <- 10
OTDIA_15k_10_filter$method <- "15k"

OTDIA_15k_100_filter <- 
  filter_pep(OTDIA_15k_100)
OTDIA_15k_100_filter$input <- 100
OTDIA_15k_100_filter$method <- "15k"

#30k
OTDIA_30k_1_filter <- 
  filter_pep(OTDIA_30k_1)
OTDIA_30k_1_filter$input <- 1
OTDIA_30k_1_filter$method <- "30k"

OTDIA_30k_5_filter <- 
  filter_pep(OTDIA_30k_5)
OTDIA_30k_5_filter$input <- 5
OTDIA_30k_5_filter$method <- "30k"

OTDIA_30k_10_filter <- 
  filter_pep(OTDIA_30k_10)
OTDIA_30k_10_filter$input <- 10
OTDIA_30k_10_filter$method <- "30k"

OTDIA_30k_100_filter <- 
  filter_pep(OTDIA_30k_100)
OTDIA_30k_100_filter$input <- 100
OTDIA_30k_100_filter$method <- "30k"
```

LIT and OT data are joined.

```{r}
LIT <- rbind(LITDIA_Turbo_1_filter,
      LITDIA_Turbo_5_filter, 
      LITDIA_Turbo_10_filter,
      LITDIA_Turbo_100_filter,
      LITDIA_Rapid_1_filter,
      LITDIA_Rapid_5_filter,
      LITDIA_Rapid_10_filter,
      LITDIA_Rapid_100_filter,
      LITDIA_Normal_1_filter,
      LITDIA_Normal_5_filter,
      LITDIA_Normal_10_filter,
      LITDIA_Normal_100_filter)
LIT$mass_analyzer <- "LIT"

OT <- rbind(OTDIA_7k_1_filter,
      OTDIA_7k_5_filter, 
      OTDIA_7k_10_filter,
      OTDIA_7k_100_filter,
      OTDIA_15k_1_filter,
      OTDIA_15k_5_filter,
      OTDIA_15k_10_filter,
      OTDIA_15k_100_filter,
      OTDIA_30k_1_filter,
      OTDIA_30k_5_filter,
      OTDIA_30k_10_filter,
      OTDIA_30k_100_filter)
OT$mass_analyzer <- "OT"

LITvsOT <- rbind(LIT, OT)

colnames(LITvsOT)[3:6] <- paste("Replicate", colnames(LITvsOT)[3:6], sep = "_")
```

```{r}
LITvsOT_prot <- LITvsOT %>% 
  group_by(input, method, mass_analyzer) %>% 
  summarise(prot_nbr = n_distinct(consensus_PG)) %>% 
  as.data.frame()

LITvsOT_prot$method <- factor(LITvsOT_prot$method, levels = c("7.5k", "15k", "30k", "Turbo", "Rapid", "Normal"))

fig_sup4 <- LITvsOT_prot %>% 
  ggplot(aes(x = input, y = prot_nbr, color = method, group = method)) +
  geom_line(size = 2.5)+
  geom_point(size = 4)+
  scale_color_manual(values = c("#ADC2E8", "#7F9FDB", "#527DCE", "#EEB9CF", "#DF7FA7", "#D35087"))+
  scale_x_log10(breaks = c(1, 5, 10, 100))+
  theme_bw()+
  theme(legend.position = c(0.17, 0.825),
        legend.background = element_blank(),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"),
        axis.title.y = element_text(vjust = 2),
        plot.margin = margin(t = 30,
                             r = 5.5,
                             b = 5.5,
                             l = 5.5))+
  labs(x = "Input (ng)",
       y = "Identified proteins groups",
       color = "Methods")

#save as pdf
#cairo_pdf(filename = "fig_sup4.pdf", width = 7.81, height = 6.46)
#fig_sup4
#dev.off()
```