---
title: "Fig. 4 Comparison of windowing scheme."
author: "Samuel Grégoire & Lukas R. Woltereck"
output:
  rmarkdown::github_document
---


Fig. 4 Comparison of windowing scheme.

 Comparison of the number of identified peptides on LIT-DIA-based method on Normal scanning mode with constant auto-IIT and different numbers of windows (34, 40, and 45 windows) and input material (low, and high-input tryptic HeLa digest) on WhisperTM 100 for 40 SPD and 20 SPD. Identified peptides with a coefficient of variation (CV) between 10% and 15% are coloured with light red and those with a CV below 10% with dark red.

# Load packages

```{r, message = FALSE}
library("tidyverse")

#set bw theme as default theme
theme_set(theme_bw())
```

# Load data

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
```

```{r}
#lit_path <- "C:/Data/LIT/"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606) in csv files and need to be loaded in RStudio with the function `read.csv2()`.

## 20 SPD

```{r}
#1 ng
LITDIA_Normal_20SPD_34w_1 <- read.csv2(paste0(lit_path, "20220218_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto_34w.csv"))
LITDIA_Normal_20SPD_40w_1 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_20SPD_45w_1 <- read.csv2(paste0(lit_path, "20220218_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto_45w.csv"))

#100 ng
LITDIA_Normal_20SPD_34w_100 <- read.csv2(paste0(lit_path, "20220601_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_34w.csv"))
LITDIA_Normal_20SPD_40w_100 <- read.csv2(paste0(lit_path, "20220413_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_40w.csv"))
LITDIA_Normal_20SPD_45w_100 <- read.csv2(paste0(lit_path, "20220418_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_45w.csv"))
```

## 40SPD

```{r}
#1 ng
LITDIA_Normal_34w_1 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto_34w.csv"))
LITDIA_Normal_40w_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_45w_1 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto_45w.csv"))

#100 ng
LITDIA_Normal_34w_100 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto_34w.csv"))
LITDIA_Normal_40w_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_45w_100 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto_45w.csv"))
```

# Clean data tables

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It also calculates the mean between the four replicates. Spectronaut does some imputation by default, but we want to keep missing values. Imputed values are replaced by NA. Peptides missing in more than one replicate are highlighted as TRUE.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  x_clean_with_mean <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  x_filter_highlight <- x_clean_with_mean %>% 
  mutate(na_nbr = rowSums(is.na(x_clean_with_mean[-1]))) %>%
  mutate(mean_quantity = 
           rowMeans(x_clean_with_mean[2:ncol(x_clean_with_mean)], 
                    na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("
Highlighted ", sum(x_filter_highlight$filtered) , " peptide(s) found in less than ", ncol(x_clean_with_mean) -2, " replicates")
  
  return(x_filter_highlight)
}
```

The `filter_pep()` function is used for every data-set.

## 20 SPD

```{r}
#1 ng
LITDIA_Normal_20SPD_34w_1 <-  filter_pep(LITDIA_Normal_20SPD_34w_1)
LITDIA_Normal_20SPD_40w_1 <-  filter_pep(LITDIA_Normal_20SPD_40w_1)
LITDIA_Normal_20SPD_45w_1 <-  filter_pep(LITDIA_Normal_20SPD_45w_1)

#100 ng
LITDIA_Normal_20SPD_34w_100 <-  filter_pep(LITDIA_Normal_20SPD_34w_100)
LITDIA_Normal_20SPD_40w_100 <-  filter_pep(LITDIA_Normal_20SPD_40w_100)
LITDIA_Normal_20SPD_45w_100 <-  filter_pep(LITDIA_Normal_20SPD_45w_100)
```

## 40 SPD

```{r}
#1 ng
LITDIA_Normal_34w_1 <-  filter_pep(LITDIA_Normal_34w_1)
LITDIA_Normal_40w_1 <-  filter_pep(LITDIA_Normal_40w_1)
LITDIA_Normal_45w_1 <-  filter_pep(LITDIA_Normal_45w_1)

#100 ng
LITDIA_Normal_34w_100 <-  filter_pep(LITDIA_Normal_34w_100)
LITDIA_Normal_40w_100 <-  filter_pep(LITDIA_Normal_40w_100)
LITDIA_Normal_45w_100 <-  filter_pep(LITDIA_Normal_45w_100)
```

# Count number of identified peptides

Empty vectors are created to store the number of identified peptides in
each replicates for each data-set.

```{r}
id_LITDIA_Normal_20SPD_34w_1 <- id_LITDIA_Normal_20SPD_40w_1 <-
  id_LITDIA_Normal_20SPD_45w_1 <- id_LITDIA_Normal_20SPD_34w_100 <- 
  id_LITDIA_Normal_20SPD_40w_100 <- id_LITDIA_Normal_20SPD_45w_100 <- 
  id_LITDIA_Normal_34w_1 <- id_LITDIA_Normal_40w_1 <-
  id_LITDIA_Normal_45w_1 <- id_LITDIA_Normal_34w_100 <-
  id_LITDIA_Normal_40w_100 <- id_LITDIA_Normal_45w_100 <- rep(NA, 4)
```

The numbers of identified peptides are counted by summing non-missing
values for each replicate and stored in the vectors created above.

## 20 SPD

```{r}
#1 ng
for(i in 2:5){
  id_LITDIA_Normal_20SPD_34w_1[i-1] <- 
    sum(!is.na(LITDIA_Normal_20SPD_34w_1[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_40w_1[i-1] <- 
    sum(!is.na(LITDIA_Normal_20SPD_40w_1[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_45w_1[i-1] <- 
    sum(!is.na(LITDIA_Normal_20SPD_45w_1[, i]))}

#100 ng
for(i in 2:5){
  id_LITDIA_Normal_20SPD_34w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_34w_100[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_40w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_40w_100[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_45w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_45w_100[, i]))}
```

## 40 SPD

```{r}
#1 ng
for(i in 2:5){
  id_LITDIA_Normal_34w_1[i-1] <- sum(!is.na(LITDIA_Normal_34w_1[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_40w_1[i-1] <- sum(!is.na(LITDIA_Normal_40w_1[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_45w_1[i-1] <- sum(!is.na(LITDIA_Normal_45w_1[, i]))}

#100 ng
for(i in 2:5){
  id_LITDIA_Normal_34w_100[i-1] <- sum(!is.na(LITDIA_Normal_34w_100[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_40w_100[i-1] <- sum(!is.na(LITDIA_Normal_40w_100[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_45w_100[i-1] <- sum(!is.na(LITDIA_Normal_45w_100[, i]))}
```

# Compute CV

The function `compute_CV()` below takes the data-sets, already filtered by `filter_pep()`, as an entry and compute the coefficients of variation (CV) for the replicates of each method. Most of our data-sets include four replicates but some contain only three. In this case, an empty column is added as a fourth replicate to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the method, the number of samples per day and the input are included afterwards.

## 20 SPD

```{r}
LITDIA_Normal_20SPD_34w_1_cv <- compute_CV(LITDIA_Normal_20SPD_34w_1)
LITDIA_Normal_20SPD_34w_1_cv$method <- 34
LITDIA_Normal_20SPD_34w_1_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_34w_1_cv$input<- "1 ng"
LITDIA_Normal_20SPD_34w_100_cv <- compute_CV(LITDIA_Normal_20SPD_34w_100)
LITDIA_Normal_20SPD_34w_100_cv$method <- 34
LITDIA_Normal_20SPD_34w_100_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_34w_100_cv$input<- "100 ng"
LITDIA_Normal_20SPD_40w_1_cv <- compute_CV(LITDIA_Normal_20SPD_40w_1)
LITDIA_Normal_20SPD_40w_1_cv$method <- 40
LITDIA_Normal_20SPD_40w_1_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_40w_1_cv$input<- "1 ng"
LITDIA_Normal_20SPD_40w_100_cv <- compute_CV(LITDIA_Normal_20SPD_40w_100)
LITDIA_Normal_20SPD_40w_100_cv$method <- 40
LITDIA_Normal_20SPD_40w_100_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_40w_100_cv$input<- "100 ng"
LITDIA_Normal_20SPD_45w_1_cv <- compute_CV(LITDIA_Normal_20SPD_45w_1)
LITDIA_Normal_20SPD_45w_1_cv$method <- 45
LITDIA_Normal_20SPD_45w_1_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_45w_1_cv$input<- "1 ng"
LITDIA_Normal_20SPD_45w_100_cv <- compute_CV(LITDIA_Normal_20SPD_45w_100)
LITDIA_Normal_20SPD_45w_100_cv$method <- 45
LITDIA_Normal_20SPD_45w_100_cv$spd<- "20 SPD"
LITDIA_Normal_20SPD_45w_100_cv$input<- "100 ng"
```

## 40 SPD

```{r}
LITDIA_Normal_34w_1_cv <- compute_CV(LITDIA_Normal_34w_1)
LITDIA_Normal_34w_1_cv$method <- 34
LITDIA_Normal_34w_1_cv$spd<- "40 SPD"
LITDIA_Normal_34w_1_cv$input<- "1 ng"
LITDIA_Normal_34w_100_cv <- compute_CV(LITDIA_Normal_34w_100)
LITDIA_Normal_34w_100_cv$method <- 34
LITDIA_Normal_34w_100_cv$spd<- "40 SPD"
LITDIA_Normal_34w_100_cv$input<- "100 ng"
LITDIA_Normal_40w_1_cv <- compute_CV(LITDIA_Normal_40w_1)
LITDIA_Normal_40w_1_cv$method <- 40
LITDIA_Normal_40w_1_cv$spd<- "40 SPD"
LITDIA_Normal_40w_1_cv$input<- "1 ng"
LITDIA_Normal_40w_100_cv <- compute_CV(LITDIA_Normal_40w_100)
LITDIA_Normal_40w_100_cv$method <- 40
LITDIA_Normal_40w_100_cv$spd<- "40 SPD"
LITDIA_Normal_40w_100_cv$input<- "100 ng"
LITDIA_Normal_45w_1_cv <- compute_CV(LITDIA_Normal_45w_1)
LITDIA_Normal_45w_1_cv$method <- 45
LITDIA_Normal_45w_1_cv$spd<- "40 SPD"
LITDIA_Normal_45w_1_cv$input<- "1 ng"
LITDIA_Normal_45w_100_cv <- compute_CV(LITDIA_Normal_34w_100)
LITDIA_Normal_45w_100_cv$method <- 45
LITDIA_Normal_45w_100_cv$spd<- "40 SPD"
LITDIA_Normal_45w_100_cv$input<- "100 ng"
```

# Join

Data frames containing CV are combined with the function `rbind()`.

```{r}
join_fig4 <- 
  rbind(LITDIA_Normal_20SPD_34w_1_cv, LITDIA_Normal_20SPD_34w_100_cv, 
        LITDIA_Normal_20SPD_40w_1_cv, LITDIA_Normal_20SPD_40w_100_cv, 
        LITDIA_Normal_20SPD_45w_1_cv, LITDIA_Normal_20SPD_45w_100_cv, 
        LITDIA_Normal_34w_1_cv, LITDIA_Normal_34w_100_cv, 
        LITDIA_Normal_40w_1_cv, LITDIA_Normal_40w_100_cv, 
        LITDIA_Normal_45w_1_cv, LITDIA_Normal_45w_100_cv)

join_fig4$method %>% table()
join_fig4$input %>% table()
join_fig4$spd %>% table()

# Factorise to set order
join_fig4$method <- factor(join_fig4$method, 
                          levels = unique(join_fig4$method))
join_fig4$input <- factor(join_fig4$input, 
                          levels = unique(join_fig4$input))
join_fig4$spd <- factor(join_fig4$spd, 
                          levels = c("40 SPD", "20 SPD"))
```

A new column called “CV_filter” is added to identify peptides with a CV over 0.15 (1), between 0.1 and 0.15 (2) and under 0.1 (3).

```{r}
join_fig4$CV_filter <- NA
join_fig4$CV_filter[join_fig4$CV < 0.1] <- "3"
join_fig4$CV_filter[join_fig4$CV >= 0.1 & join_fig4$CV <= 0.15] <- "2"
join_fig4$CV_filter[join_fig4$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out. The number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method.

```{r}
join_fig4 <- join_fig4 %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(method, spd, input, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))
join_fig4$id_S4[join_fig4$id_S4 == 0] <- NA 
join_fig4$mean_id <- rowMeans(join_fig4[5:8], na.rm = TRUE)
join_fig4$sd_id <- apply(join_fig4[5:8], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

# Plot

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot2`. Error bars representing the standard deviation are displayed using `geom_errorbar()`. Due to the “stacked” aspect of the col plot, error bars y position is adjusted by using the y_errorbar variable instead of the mean_id.

```{r}
join_fig4$y_errorbar <- join_fig4$mean_id
join_fig4$y_errorbar[join_fig4$CV_filter == "1"] <-
  join_fig4$y_errorbar[join_fig4$CV_filter == "1"] +
  join_fig4$y_errorbar[join_fig4$CV_filter == "2"]+
  join_fig4$y_errorbar[join_fig4$CV_filter == "3"]
join_fig4$y_errorbar[join_fig4$CV_filter == "2"] <-
  join_fig4$y_errorbar[join_fig4$CV_filter == "2"]+
  join_fig4$y_errorbar[join_fig4$CV_filter == "3"]
figure4 <- join_fig4 %>% 
  ggplot(aes(x = method, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
 facet_grid(input~spd)+
  labs(x = "Number of Windows",
       y = "Identified peptides",
       fill = "CV") +
  theme_bw() +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"),
        legend.position = "top")+
  scale_fill_manual(values = c("grey82", "#ffaa8b", "#ff713e"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 16000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)
figure4

#Save as pdf
#cairo_pdf(filename = "fig4.pdf", width = 18.75, height = 12.5)
#figure4
#dev.off()
```

# Session information

```{r, echo = FALSE}
sessionInfo()
```

