---
title: "Figure S7 Comparison of low-input protein identifications between SpectronautTM version 15 and 16"
author: "Lukas R. Woltereck & Samuel Grégoire"
output:
  rmarkdown::github_document
---

Supporting figure S7 Comparison of low-input protein identifications between SpectronautTM version 15 and 16. Comparison of the number of identified peptides in serial dilution (1,10, and 100 ng) of HeLa tryptic digested analyzed by DIA-LIT-based methods with Normal scanning mode on 40 SPD between Spectronaut version 15 and 16.


Comparison of the number of identified peptides in serial dilution (1,10, and 100 ng) of HeLa tryptic digested analyzed by DIA-LIT-based methods with Normal scanning mode on 40 SPD between Spectronaut version 15 and 16.

# Load packages

```{r, message = FALSE}
library("tidyverse")
library("patchwork")

#set bw theme as default theme
theme_set(theme_bw())
```

# Load data

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgregoire/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
```

```{r}
#lit_path <- "C:/Data/LIT/"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606) in csv files and need to be loaded in RStudio with the function `read.csv2()`.Data tables were exported from Spectronaut (version 15.5.211111.50606 or 16.0.220606.53000) in csv files and need to be loaded in RStudio with the function `read.csv2()`.

## Spectronaut V.15

```{r}
#Turbo
LITDIA_Turbo_1_SN15 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_10_SN15 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_100_SN15 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
#Rapid
LITDIA_Rapid_1_SN15 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_10_SN15 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_100_SN15 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
#Normal
LITDIA_Normal_1_SN15 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_10_SN15 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_100_SN15 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

## Spectronaut V.16

```{r}
#Turbo
LITDIA_Turbo_1_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Turbo_1CV_1ng_auto_40w.csv"))
LITDIA_Turbo_10_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Turbo_1CV_10ng_auto_40w.csv"))
LITDIA_Turbo_100_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Turbo_1CV_100ng_auto_40w.csv"))
#Rapid
LITDIA_Rapid_1_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Rapid_1CV_1ng_auto_40w.csv"))
LITDIA_Rapid_10_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Rapid_1CV_10ng_auto_40w.csv"))
LITDIA_Rapid_100_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Rapid_1CV_100ng_auto_40w.csv"))
#Normal
LITDIA_Normal_1_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Normal_1CV_1ng_auto_40w.csv"))
LITDIA_Normal_10_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Normal_1CV_10ng_auto_40w.csv"))
LITDIA_Normal_100_SN16 <- read.csv2(paste0(lit_path, "20220615_SN16_40SPD_LIT_Normal_1CV_100ng_auto_40w.csv"))
```

# Clean data tables

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It is also calculating the mean between the four replicates. Spectronaut does imputation by default, but we want to keep missing values. Imputed values are replaced by *NA*. Peptides missing in more than one replicate are highlighted as *TRUE*.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  x_clean_with_mean <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  x_filter_highlight <- x_clean_with_mean %>% 
  mutate(na_nbr = rowSums(is.na(x_clean_with_mean[-1]))) %>%
  mutate(mean_quantity = 
           rowMeans(x_clean_with_mean[2:ncol(x_clean_with_mean)], 
                    na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("
Highlighted ", sum(x_filter_highlight$filtered) , " peptide(s) found in less than ", ncol(x_clean_with_mean) -2, " replicates")
  
  return(x_filter_highlight)
}
```

## Spectronaut V.15

```{r}
LITDIA_Turbo_1_SN15 <-  filter_pep(LITDIA_Turbo_1_SN15)
LITDIA_Turbo_10_SN15 <-  filter_pep(LITDIA_Turbo_10_SN15)
LITDIA_Turbo_100_SN15 <-  filter_pep(LITDIA_Turbo_100_SN15)

LITDIA_Rapid_1_SN15 <-  filter_pep(LITDIA_Rapid_1_SN15)
LITDIA_Rapid_10_SN15 <-  filter_pep(LITDIA_Rapid_10_SN15)
LITDIA_Rapid_100_SN15 <-  filter_pep(LITDIA_Rapid_100_SN15)

LITDIA_Normal_1_SN15 <-  filter_pep(LITDIA_Normal_1_SN15)
LITDIA_Normal_10_SN15 <-  filter_pep(LITDIA_Normal_10_SN15)
LITDIA_Normal_100_SN15 <-  filter_pep(LITDIA_Normal_100_SN15)
```

## Spectronaut V.16

```{r}
LITDIA_Turbo_1_SN16 <-  filter_pep(LITDIA_Turbo_1_SN16)
LITDIA_Turbo_10_SN16 <-  filter_pep(LITDIA_Turbo_10_SN16)
LITDIA_Turbo_100_SN16 <-  filter_pep(LITDIA_Turbo_100_SN16)

LITDIA_Rapid_1_SN16 <-  filter_pep(LITDIA_Rapid_1_SN16)
LITDIA_Rapid_10_SN16 <-  filter_pep(LITDIA_Rapid_10_SN16)
LITDIA_Rapid_100_SN16 <-  filter_pep(LITDIA_Rapid_100_SN16)

LITDIA_Normal_1_SN16 <-  filter_pep(LITDIA_Normal_1_SN16)
LITDIA_Normal_10_SN16 <-  filter_pep(LITDIA_Normal_10_SN16)
LITDIA_Normal_100_SN16 <-  filter_pep(LITDIA_Normal_100_SN16)
```

# Count number of identified peptides

Empty vectors are created to store the number of identified peptides in each replicates for each data-set.

```{r}
id_LITDIA_Turbo_1_SN15 <- id_LITDIA_Turbo_10_SN15 <- id_LITDIA_Turbo_100_SN15 <-
id_LITDIA_Rapid_1_SN15 <- id_LITDIA_Rapid_10_SN15 <- id_LITDIA_Rapid_100_SN15 <-
id_LITDIA_Normal_1_SN15 <- id_LITDIA_Normal_10_SN15 <- id_LITDIA_Normal_100_SN15 <-
id_LITDIA_Turbo_1_SN16 <- id_LITDIA_Turbo_10_SN16 <- id_LITDIA_Turbo_100_SN16 <-
id_LITDIA_Rapid_1_SN16 <- id_LITDIA_Rapid_10_SN16 <- id_LITDIA_Rapid_100_SN16 <-
id_LITDIA_Normal_1_SN16 <- id_LITDIA_Normal_10_SN16 <- id_LITDIA_Normal_100_SN16 <- rep(NA, 4)
```

The numbers of identified peptides are counted by summing non-missing values for each replicate and stored in the vectors created above.

## Spectronaut V.15

```{r}
#Turbo
for(i in 2:5){
  id_LITDIA_Turbo_1_SN15[i-1] <- sum(!is.na(LITDIA_Turbo_1_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Turbo_10_SN15[i-1] <- sum(!is.na(LITDIA_Turbo_10_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Turbo_100_SN15[i-1] <- sum(!is.na(LITDIA_Turbo_100_SN15[, i]))}

#Rapid
for(i in 2:5){
  id_LITDIA_Rapid_1_SN15[i-1] <- sum(!is.na(LITDIA_Rapid_1_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Rapid_10_SN15[i-1] <- sum(!is.na(LITDIA_Rapid_10_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Rapid_100_SN15[i-1] <- sum(!is.na(LITDIA_Rapid_100_SN15[, i]))}

#Normal
for(i in 2:5){
  id_LITDIA_Normal_1_SN15[i-1] <- sum(!is.na(LITDIA_Normal_1_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_10_SN15[i-1] <- sum(!is.na(LITDIA_Normal_10_SN15[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_100_SN15[i-1] <- sum(!is.na(LITDIA_Normal_100_SN15[, i]))}
```

## Spectronaut V.16

```{r}
#Turbo
for(i in 2:5){
  id_LITDIA_Turbo_1_SN16[i-1] <- sum(!is.na(LITDIA_Turbo_1_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Turbo_10_SN16[i-1] <- sum(!is.na(LITDIA_Turbo_10_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Turbo_100_SN16[i-1] <- sum(!is.na(LITDIA_Turbo_100_SN16[, i]))}

#Rapid
for(i in 2:5){
  id_LITDIA_Rapid_1_SN16[i-1] <- sum(!is.na(LITDIA_Rapid_1_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Rapid_10_SN16[i-1] <- sum(!is.na(LITDIA_Rapid_10_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Rapid_100_SN16[i-1] <- sum(!is.na(LITDIA_Rapid_100_SN16[, i]))}

#Normal
for(i in 2:5){
  id_LITDIA_Normal_1_SN16[i-1] <- sum(!is.na(LITDIA_Normal_1_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_10_SN16[i-1] <- sum(!is.na(LITDIA_Normal_10_SN16[, i]))}
for(i in 2:5){
  id_LITDIA_Normal_100_SN16[i-1] <- sum(!is.na(LITDIA_Normal_100_SN16[, i]))}
```

# Compute CV

The function `compute_CV()` below takes the data-sets, already filtered by `filter_pep()`, as an entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our data-sets include four replicates but some contain only three. In this case, an empty column is added as a fourth replicate to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the scanning mode, the Scectronaut version and the input are included afterwards.

## Spectronaut V.15

```{r}
#Turbo
LITDIA_Turbo_1_SN15_cv <- compute_CV(LITDIA_Turbo_1_SN15)
LITDIA_Turbo_1_SN15_cv$input<- "1 ng"
LITDIA_Turbo_1_SN15_cv$version<- 15
LITDIA_Turbo_1_SN15_cv$scanning_mode<- "Turbo"
LITDIA_Turbo_10_SN15_cv <- compute_CV(LITDIA_Turbo_10_SN15)
LITDIA_Turbo_10_SN15_cv$input<- "10 ng"
LITDIA_Turbo_10_SN15_cv$version<- 15
LITDIA_Turbo_10_SN15_cv$scanning_mode<- "Turbo"
LITDIA_Turbo_100_SN15_cv <- compute_CV(LITDIA_Turbo_100_SN15)
LITDIA_Turbo_100_SN15_cv$input<- "100 ng"
LITDIA_Turbo_100_SN15_cv$version<- 15
LITDIA_Turbo_100_SN15_cv$scanning_mode<- "Turbo"

#Rapid
LITDIA_Rapid_1_SN15_cv <- compute_CV(LITDIA_Rapid_1_SN15)
LITDIA_Rapid_1_SN15_cv$input<- "1 ng"
LITDIA_Rapid_1_SN15_cv$version<- 15
LITDIA_Rapid_1_SN15_cv$scanning_mode<- "Rapid"
LITDIA_Rapid_10_SN15_cv <- compute_CV(LITDIA_Rapid_10_SN15)
LITDIA_Rapid_10_SN15_cv$input<- "10 ng"
LITDIA_Rapid_10_SN15_cv$version<- 15
LITDIA_Rapid_10_SN15_cv$scanning_mode<- "Rapid"
LITDIA_Rapid_100_SN15_cv <- compute_CV(LITDIA_Rapid_100_SN15)
LITDIA_Rapid_100_SN15_cv$input<- "100 ng"
LITDIA_Rapid_100_SN15_cv$version<- 15
LITDIA_Rapid_100_SN15_cv$scanning_mode<- "Rapid"

#Normal
LITDIA_Normal_1_SN15_cv <- compute_CV(LITDIA_Normal_1_SN15)
LITDIA_Normal_1_SN15_cv$input<- "1 ng"
LITDIA_Normal_1_SN15_cv$version<- 15
LITDIA_Normal_1_SN15_cv$scanning_mode<- "Normal"
LITDIA_Normal_10_SN15_cv <- compute_CV(LITDIA_Normal_10_SN15)
LITDIA_Normal_10_SN15_cv$input<- "10 ng"
LITDIA_Normal_10_SN15_cv$version<- 15
LITDIA_Normal_10_SN15_cv$scanning_mode<- "Normal"
LITDIA_Normal_100_SN15_cv <- compute_CV(LITDIA_Normal_100_SN15)
LITDIA_Normal_100_SN15_cv$input<- "100 ng"
LITDIA_Normal_100_SN15_cv$version<- 15
LITDIA_Normal_100_SN15_cv$scanning_mode<- "Normal"
```

## Spectronaut V.16

```{r}
#Turbo
LITDIA_Turbo_1_SN16_cv <- compute_CV(LITDIA_Turbo_1_SN16)
LITDIA_Turbo_1_SN16_cv$input<- "1 ng"
LITDIA_Turbo_1_SN16_cv$version<- 16
LITDIA_Turbo_1_SN16_cv$scanning_mode<- "Turbo"
LITDIA_Turbo_10_SN16_cv <- compute_CV(LITDIA_Turbo_10_SN16)
LITDIA_Turbo_10_SN16_cv$input<- "10 ng"
LITDIA_Turbo_10_SN16_cv$version<- 16
LITDIA_Turbo_10_SN16_cv$scanning_mode<- "Turbo"
LITDIA_Turbo_100_SN16_cv <- compute_CV(LITDIA_Turbo_100_SN16)
LITDIA_Turbo_100_SN16_cv$input<- "100 ng"
LITDIA_Turbo_100_SN16_cv$version<- 16
LITDIA_Turbo_100_SN16_cv$scanning_mode<- "Turbo"

#Rapid
LITDIA_Rapid_1_SN16_cv <- compute_CV(LITDIA_Rapid_1_SN16)
LITDIA_Rapid_1_SN16_cv$input<- "1 ng"
LITDIA_Rapid_1_SN16_cv$version<- 16
LITDIA_Rapid_1_SN16_cv$scanning_mode<- "Rapid"
LITDIA_Rapid_5_SN16_cv <- compute_CV(LITDIA_Rapid_1_SN16)
LITDIA_Rapid_10_SN16_cv <- compute_CV(LITDIA_Rapid_10_SN16)
LITDIA_Rapid_10_SN16_cv$input<- "10 ng"
LITDIA_Rapid_10_SN16_cv$version<- 16
LITDIA_Rapid_10_SN16_cv$scanning_mode<- "Rapid"
LITDIA_Rapid_100_SN16_cv <- compute_CV(LITDIA_Rapid_100_SN16)
LITDIA_Rapid_100_SN16_cv$input<- "100 ng"
LITDIA_Rapid_100_SN16_cv$version<- 16
LITDIA_Rapid_100_SN16_cv$scanning_mode<- "Rapid"

#Normal
LITDIA_Normal_1_SN16_cv <- compute_CV(LITDIA_Normal_1_SN16)
LITDIA_Normal_1_SN16_cv$input<- "1 ng"
LITDIA_Normal_1_SN16_cv$version<- 16
LITDIA_Normal_1_SN16_cv$scanning_mode<- "Normal"
LITDIA_Normal_10_SN16_cv <- compute_CV(LITDIA_Normal_10_SN16)
LITDIA_Normal_10_SN16_cv$input<- "10 ng"
LITDIA_Normal_10_SN16_cv$version<- 16
LITDIA_Normal_10_SN16_cv$scanning_mode<- "Normal"
LITDIA_Normal_100_SN16_cv <- compute_CV(LITDIA_Normal_100_SN16)
LITDIA_Normal_100_SN16_cv$input<- "100 ng"
LITDIA_Normal_100_SN16_cv$version<- 16
LITDIA_Normal_100_SN16_cv$scanning_mode<- "Normal"
```

# Join

Data frames containing CV are combined with the function `rbind()`.

```{r}
id_figure8 <- 
rbind(LITDIA_Turbo_1_SN15_cv, LITDIA_Turbo_10_SN15_cv, LITDIA_Turbo_100_SN15_cv,
LITDIA_Rapid_1_SN15_cv, LITDIA_Rapid_10_SN15_cv, LITDIA_Rapid_100_SN15_cv,
LITDIA_Normal_1_SN15_cv, LITDIA_Normal_10_SN15_cv, LITDIA_Normal_100_SN15_cv,
LITDIA_Turbo_1_SN16_cv,LITDIA_Turbo_10_SN16_cv, LITDIA_Turbo_100_SN16_cv,
LITDIA_Rapid_1_SN16_cv, LITDIA_Rapid_10_SN16_cv, LITDIA_Rapid_100_SN16_cv,
LITDIA_Normal_1_SN16_cv, LITDIA_Normal_10_SN16_cv, LITDIA_Normal_100_SN16_cv)
# Factorise to set order
id_figure8$input <- factor(id_figure8$input, 
                          levels = unique(id_figure8$input))
id_figure8$scanning_mode <- factor(id_figure8$scanning_mode, 
                          levels = unique(id_figure8$scanning_mode))
id_figure8$version <- factor(id_figure8$version, 
                          levels = unique(id_figure8$version))
```

A new column called “CV_filter” is added to identify peptides with a CV over 0.15 (1), between 0.1 and 0.15 (2) and under 0.1 (3).

```{r}
id_figure8$CV_filter <- NA
id_figure8$CV_filter[id_figure8$CV < 0.1] <- "3"
id_figure8$CV_filter[id_figure8$CV >= 0.1 & id_figure8$CV <= 0.15] <- "2"
id_figure8$CV_filter[id_figure8$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out. The number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method.

```{r}
id_figure8 <- id_figure8 %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(input, CV_filter, scanning_mode, version) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))

id_figure8$id_S4[id_figure8$id_S4 == 0] <- NA

#Calculating mean and sd from the replicates 
id_figure8$mean_id <- rowMeans(id_figure8[5:8], na.rm = TRUE)
id_figure8$sd_id <- apply(id_figure8[5:8], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

# Plot

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot2`. Error bars representing the standard deviation are displayed using `geom_errorbar()`. Due to the “stacked” aspect of the col plot, error bars y position is adjusted by using the y_errorbar variable instead of the mean_id.

```{r}
id_figure8$y_errorbar <- id_figure8$mean_id
id_figure8$y_errorbar[id_figure8$CV_filter == "1"] <-
  id_figure8$y_errorbar[id_figure8$CV_filter == "1"] +
  id_figure8$y_errorbar[id_figure8$CV_filter == "2"]+
  id_figure8$y_errorbar[id_figure8$CV_filter == "3"]
id_figure8$y_errorbar[id_figure8$CV_filter == "2"] <-
  id_figure8$y_errorbar[id_figure8$CV_filter == "2"]+
  id_figure8$y_errorbar[id_figure8$CV_filter == "3"]
figure8 <- id_figure8 %>%
  ggplot(aes(x = version, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
  labs(x = "Spectronaut version",
       y = "Identified peptides",
       fill = "CV") +
  facet_grid(input~scanning_mode)+
  scale_y_continuous(limits = c(0, 12500))+
  theme_bw() +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"),
        legend.position = "top")+
  scale_fill_manual(values = c("grey82", "#ffaa8b", "#ff713e"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)
figure8

#save as pdf
#cairo_pdf(filename = "fig8.pdf", width = 18.75, height = 13.02)
#figure8
#dev.off()
```


# Session information

```{r, echo = FALSE}
sessionInfo()
```


    