---
title: "Fig. 3 Increasing injection time on DIA LIT methods"
autor: "Samuel Grégoire & Lukas R. Woltereck"
output: github_document
  #html_document:
   # keep_md: true
   # toc: true
    #toc_float: true
    #theme: cerulean
    #highlight: kate
    #fig_width: 9
    #fig_height : 7
    #df_print: paged
    #number_sections: true
    #fig_crop: no
---

# Load packages

```{r, message=FALSE}
library("tidyverse")
library("patchwork")
#set bw theme as default theme
theme_set(theme_bw())
```

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <-"C:/Users/lukwolt/Documents/R/LIT/"
ppp_path <- "C:/Users/lukwolt/Documents/R/Points_across_a_peak/"
```

```{r, eval = FALSE}
lit_path <- "C://data/lit"
ppp_path <- "C://data/ppp"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606) in csv files and need to be loaded in RStudio with the function `read.csv2()`.

# Figure A

Comparison of the number of identified peptides on DIA-LIT-based method on Normal scanning mode for WhisperTM 100 20 SPD from 1 ng of tryptic HeLa lysate with different ITs at fixed 40 isolation windows. Identified peptides with a coefficient of variation (CV) between 10% and 15% are colored with light red and those with a CV below 10% with dark red. The cycle times for the methods are indicated by their injection times: 38 ms 2.4 s, for 60 ms 3.28 s, for 80 ms 4.09 s, and for 100 ms 4.91 s.

# Load data A

```{r}
LITDIA_Normal_20SPD_60ms <- read.csv2(paste0(lit_path, "20220215_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV45_60ms.csv"))
LITDIA_Normal_20SPD_80ms <- read.csv2(paste0(lit_path, "20220215_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV45_80ms.csv"))
LITDIA_Normal_20SPD_100ms <- read.csv2(paste0(lit_path, "20220215_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV45_100ms.csv"))
LITDIA_Normal_20SPD_38ms <- read.csv2(paste0(lit_path, "20220525_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV45_auto.csv"))
```

## Clean data tables A

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It also calculates the mean between the four replicates. Spectronaut does some imputation by default, but we want to keep missing values. Imputed values are replaced by NA. Peptides missing in more than one replicate are highlighted as TRUE.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  mutate(na_nbr = rowSums(is.na(y[-1]))) %>%
  mutate(mean_quantity = rowMeans(y[2:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("
Highlighted ", sum(z$filtered) , " peptide(s) found in less than ", ncol(y) -2, " replicates")
  
  return(z)
}
```

The `filter_pep()` function is used for every data-set.

```{r}
LITDIA_Normal_20SPD_60ms <- filter_pep(LITDIA_Normal_20SPD_60ms)
LITDIA_Normal_20SPD_80ms <- filter_pep(LITDIA_Normal_20SPD_80ms)
LITDIA_Normal_20SPD_100ms <- filter_pep(LITDIA_Normal_20SPD_100ms)
LITDIA_Normal_20SPD_38ms <- filter_pep(LITDIA_Normal_20SPD_38ms)
```

## Number of identified peptides A

Empty vectors are created to store the number of identified peptides in each replicates for each data-set.

```{r}
id_LITDIA_Normal_20SPD_60ms <- id_LITDIA_Normal_20SPD_80ms <- 
  id_LITDIA_Normal_20SPD_100ms <- id_LITDIA_Normal_20SPD_38ms <-
  rep(NA, 4)
```

The numbers of identified peptides are counted by summing non-missing values for each replicate and stored in the vectors created above.

```{r}
for(i in 2:(ncol(LITDIA_Normal_20SPD_60ms)-2)){
  id_LITDIA_Normal_20SPD_60ms[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_60ms[, i]))}
for(i in 2:(ncol(LITDIA_Normal_20SPD_80ms)-2)){
  id_LITDIA_Normal_20SPD_80ms[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_80ms[, i]))}
for(i in 2:(ncol(LITDIA_Normal_20SPD_100ms)-2)){
  id_LITDIA_Normal_20SPD_100ms[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_100ms[, i]))}
for(i in 2:(ncol(LITDIA_Normal_20SPD_38ms)-2)){
  id_LITDIA_Normal_20SPD_38ms[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_38ms[, i]))}
```

## Compute CV A

The function `compute_CV()` below takes the data-sets, already filtered by `filter_pep()`, as an entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our data-sets include four replicates but some contain only three. In this case, an empty column is added as a fourth replicate to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the injection time are included afterwards.

```{r}
LITDIA_Normal_20SPD_38ms_CV <- compute_CV(LITDIA_Normal_20SPD_38ms)
LITDIA_Normal_20SPD_38ms_CV$IT <- "38ms"
LITDIA_Normal_20SPD_60ms_CV <- compute_CV(LITDIA_Normal_20SPD_60ms)
LITDIA_Normal_20SPD_60ms_CV$IT <- "60ms"
LITDIA_Normal_20SPD_80ms_CV <- compute_CV(LITDIA_Normal_20SPD_80ms)
LITDIA_Normal_20SPD_80ms_CV$IT <- "80ms"
LITDIA_Normal_20SPD_100ms_CV <- compute_CV(LITDIA_Normal_20SPD_100ms)
LITDIA_Normal_20SPD_100ms_CV$IT <- "100ms"
```

## Join A

Data frames containing CV are combined with the function `rbind()`.

```{r}
CV_figure3 <- 
  rbind(LITDIA_Normal_20SPD_38ms_CV, LITDIA_Normal_20SPD_60ms_CV, 
        LITDIA_Normal_20SPD_80ms_CV, LITDIA_Normal_20SPD_100ms_CV)
# Factorise to set order
CV_figure3$IT <- factor(CV_figure3$IT, 
                          levels = c("38ms", "60ms", "80ms", "100ms"))
```

A new column called "CV_filter" is added to identify peptides with a CV over 0.15 (1), between 0.1 and 0.15 (2) and under 0.1 (3).

```{r}
CV_figure3$CV_filter <- NA
CV_figure3$CV_filter[CV_figure3$CV < 0.1] <- "3"
CV_figure3$CV_filter[CV_figure3$CV >= 0.1 & CV_figure3$CV <= 0.15] <- "2"
CV_figure3$CV_filter[CV_figure3$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out. The number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method.

```{r}
CV_figure3$SPD <- "20 SPD"
CV_figure3 <- CV_figure3 %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(SPD, IT, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))
CV_figure3$mean_id <- rowMeans(CV_figure3[4:7], na.rm = TRUE)
CV_figure3$sd_id <- apply(CV_figure3[4:7], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

## Plot A

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot2`. Error bars representing the standard deviation are displayed using `geom_errorbar()`. Due to the "stacked" aspect of the col plot, error bars y position is adjusted by using the y_errorbar variable instead of the mean_id.

```{r}
CV_figure3$y_errorbar <- CV_figure3$mean_id
CV_figure3$y_errorbar[CV_figure3$CV_filter == "1"] <-
  CV_figure3$y_errorbar[CV_figure3$CV_filter == "1"] +
  CV_figure3$y_errorbar[CV_figure3$CV_filter == "2"]+
  CV_figure3$y_errorbar[CV_figure3$CV_filter == "3"]
CV_figure3$y_errorbar[CV_figure3$CV_filter == "2"] <-
  CV_figure3$y_errorbar[CV_figure3$CV_filter == "2"]+
  CV_figure3$y_errorbar[CV_figure3$CV_filter == "3"]
figure3a <- CV_figure3 %>% 
  ggplot(aes(x = IT, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
  facet_grid(~SPD) +
  theme_bw() +
  labs(x = "Injection time",
       y = "Identified peptides",
       fill = "CV",
       title = "A") +
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.095),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 22),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.text.x = element_text(hjust = 0.62),
        axis.title.y = element_text(vjust = 2.2),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        legend.key.size = unit(0.9, "cm"),
        axis.title.x = element_text(vjust = -1),
        legend.position = "top",
        plot.margin = margin(b = 20,
                             l = 20))+
  scale_fill_manual(values = c("grey82", "#ff9090", "#ff3030"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 8000)) +
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)
```

# Figure B

Comparison of the number of precursors with a number of points across a peak equal to or greater than 6 on DIA-LIT-based method on *Normal* scanning mode from 1 ng input of tryptic HeLa lysate on Whisper^TM^ 100 20 SPD with different ITs (38 ms, 60 ms, 80 ms and 100 ms) at fixed 40 isolation windows.

## Load B

The data containing the number of points across the peak are exported separately from Spectronaut (version 15.5.211111.50606) as tsv file. They are loaded in RStudio with the function `read.csv2()`.

```{r}
ppp_Turbo_20SPD_1ng_38ms <- read.csv2(paste0(ppp_path, "PPP_LIT_Normal_DIA_1ng_20SPD_1CV_38ms.tsv"), sep = "/")
ppp_Turbo_20SPD_1ng_38ms$indiv <- "20SPD_1ng_38ms"
ppp_Turbo_20SPD_1ng_60ms <- read.csv2(paste0(ppp_path, "PPP_LIT_Normal_DIA_1ng_20SPD_1CV_60ms.tsv"), sep = "/")
ppp_Turbo_20SPD_1ng_60ms$indiv <- "20SPD_1ng_60ms"
ppp_Turbo_20SPD_1ng_80ms <- read.csv2(paste0(ppp_path, "PPP_LIT_Normal_DIA_1ng_20SPD_1CV_80ms.tsv"), sep = "/")
ppp_Turbo_20SPD_1ng_80ms$indiv <- "20SPD_1ng_80ms"
ppp_Turbo_20SPD_1ng_100ms <- read.csv2(paste0(ppp_path, "PPP_LIT_Normal_DIA_1ng_20SPD_1CV_100ms.tsv"), sep = "/")
ppp_Turbo_20SPD_1ng_100ms$indiv <- "20SPD_1ng_100ms"
```

## Join B

Data frames containing CV are combined with the function `rbind()`.

```{r}
colnames(ppp_Turbo_20SPD_1ng_38ms) <- colnames(ppp_Turbo_20SPD_1ng_60ms) <- colnames(ppp_Turbo_20SPD_1ng_80ms) <- colnames(ppp_Turbo_20SPD_1ng_100ms) <-
  c("Points_per_Peaks", "indiv")
ppfig3 <- rbind(ppp_Turbo_20SPD_1ng_38ms, ppp_Turbo_20SPD_1ng_60ms, ppp_Turbo_20SPD_1ng_80ms,
            ppp_Turbo_20SPD_1ng_100ms)
```

The number of samples per day and the injection time are added to the data frame and the function `factor()` is used to set the order.

```{r}
ppfig3$spd <- NA
ppfig3$spd[grepl("20SPD", ppfig3$indiv)] <- "20 SPD"
ppfig3$spd[grepl("40SPD", ppfig3$indiv)] <- "40 SPD"
ppfig3$spd <- factor(ppfig3$spd, levels = c("40 SPD", "20 SPD"))
ppfig3$IT <- NA
ppfig3$IT[grepl("38ms", ppfig3$indiv)] <- "38 ms"
ppfig3$IT[grepl("60ms", ppfig3$indiv)] <- "60 ms"
ppfig3$IT[grepl("80ms", ppfig3$indiv)] <- "80 ms"
ppfig3$IT[grepl("100ms", ppfig3$indiv)] <- "100 ms"
ppfig3$IT <- factor(ppfig3$IT, levels = unique(ppfig3$IT))
```

## Plot B

To create a stacked barplot, the data frame is separated in two different groups. `temp2` includes all peptides with at least six points across the peak. `temp1` all the others. Both are combined in `temp` with `rbind()`.

```{r}
ppfig3$acc <- ppfig3$Points_per_Peaks >= 6
temp1 <- ppfig3 %>% 
  group_by(indiv, IT, spd) %>% 
  summarise(n_prec = sum(!is.na(Points_per_Peaks)))
temp2 <- ppfig3 %>% 
  group_by(indiv, IT, spd) %>% 
  summarise(n_acc = sum(acc))
temp1$Precursors <- "< 6"
temp2$Precursors <- "\U2265 6"
colnames(temp1)[4] <- "n"
colnames(temp2)[4] <- "n"
temp1$n <- temp1$n - temp2$n
temp <- rbind(temp2, temp1)
temp$Precursors <- factor(temp$Precursors, 
                         levels = c("< 6", "\U2265 6"))
```

To visualize `temp` a stacked col plot was created, using `ggplot2`.

```{r}
figure3b <- temp %>% 
  ggplot(aes(x = IT, y = n/4, fill = Precursors, group = IT)) +
  geom_col(width = 0.7) +
  theme_bw() +
  facet_grid(~ spd)+
  labs(x = "Injection time",
       y = "Precursors number",
       title = "B",
       fill = "Points across a peak")+
  scale_fill_manual(values = c("grey82", "#ff3030"))+
  theme(plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.095),
        axis.text = element_text(size = 24),
        strip.text = element_text(size = 22),
        axis.title = element_text(size = 22),
        axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        legend.position = "top")
```

# Join A and B

Plot 3A and 3B are combined using patchwork to create figure 3 and save it as pdf.

```{r}
figure3 <- 
(figure3a + theme(plot.margin = unit(c(0,18,0,0), "pt"))) +
(figure3b + theme(plot.margin = unit(c(0,0,0,18), "pt")))
#save as pdf
cairo_pdf(filename = "Fig. 3 Increasing injection time on DIA LIT methods.pdf", width = 20.83, height = 7.81)
figure3
dev.off()
```

# Session information

```{r, echo = FALSE}
sessionInfo()
```
