---
title: "Fig. 2 Comparison of windowing scheme"
autor: "Samuel Grégoire & Lukas R. Woltereck"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
    fig_width: 9
    fig_height : 7
    df_print: paged
    number_sections: true
    fig_crop: no
---

# Load packages

```{r}
library("tidyverse")
```

# Fig. 2 Comparison of windowing scheme

Comparison of the number of identified peptides on DIA-LIT-based method on Normal scanning mode for WhisperTM 100 20 SPD from 1 ng of tryptic HeLa lysate with different ITs at fixed 40 isolation windows. Identified peptides with a coefficient of variation (CV) between 10% and 15% are colored with light red and those with a CV below 10% with dark red. The cycle times for the methods are indicated by their injection times: 38 ms 2.4 s, for 60 ms 3.28 s, for 80 ms 4.09 s, and for 100 ms 4.91 s.

# Load data

The path to every folder used is stored to keep everything compact. LIT data is stored in the folder located in lit_path. To reproduce analysis the path must be changed to corresponding path on the local computer.

```{r, echo = FALSE}
lit_path <- "C://Users/samgr/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
```

```{r, eval = FALSE}
lit_path <- "C://data/lit"
```

Data tables were exported from Spectronaut (version 15.5.211111.50606) in csv files and need to be loaded in RStudio with the function `read.csv2()`.

## 20 SPD

1 ng

```{r}
#34w
LITDIA_Normal_20SPD_34w_1 <- read.csv2(paste0(lit_path, "20220218_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto_34w.csv"))
#40w
LITDIA_Normal_20SPD_40w_1 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto.csv"))
#45w
LITDIA_Normal_20SPD_45w_1 <- read.csv2(paste0(lit_path, "20220218_LIT_Normal_DIA_1ng_20SPD_whisper100_1CV_auto_45w.csv"))
```

100 ng

```{r}
#34w
LITDIA_Normal_20SPD_34w_100 <- read.csv2(paste0(lit_path, "20220418_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_34w.csv"))
#40w
LITDIA_Normal_20SPD_40w_100 <- read.csv2(paste0(lit_path, "20220413_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_40w.csv"))
#45w
LITDIA_Normal_20SPD_45w_100 <- read.csv2(paste0(lit_path, "20220418_LIT_Normal_DIA_100ng_20SPD_whisper100_1CV_auto_45w.csv"))
```

## 40SPD

1 ng

```{r}
#34w
LITDIA_Normal_34w_1 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto_34w.csv"))
#40w
LITDIA_Normal_40w_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
#45w
LITDIA_Normal_45w_1 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto_45w.csv"))
```

100 ng

```{r}
#34w
LITDIA_Normal_34w_100 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto_34w.csv"))
#40w
LITDIA_Normal_40w_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
#45w
LITDIA_Normal_45w_100 <- read.csv2(paste0(lit_path, "20220509_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto_45w.csv"))
```

# Clean data tables

Imported tables contain a lot of information, which are not useful for our analysis. The function `filter_pep()` only keeps the file names (replicates), quantitative values for each file name, and the peptide sequence. It also calculates the mean between the four replicates. Spectronaut does some imputation by default, but we want to keep missing values. Imputed values are replaced by NA. Peptides missing in more than one replicate are highlighted as TRUE.

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  mutate(na_nbr = rowSums(is.na(y[-1]))) %>%
  mutate(mean_quantity = rowMeans(y[2:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("Highlighted ", sum(z$filtered), " peptide(s) found in less than ", ncol(y) -2, " replicates")
  
 return(z) }

```

The `filter_pep()` function is used for every data-set.

20 SPD
1 ng
```{r}
LITDIA_Normal_20SPD_34w_1 <-  filter_pep(LITDIA_Normal_20SPD_34w_1)
LITDIA_Normal_20SPD_40w_1 <-  filter_pep(LITDIA_Normal_20SPD_40w_1)
LITDIA_Normal_20SPD_45w_1 <-  filter_pep(LITDIA_Normal_20SPD_45w_1)
```

100 ng
```{r}
LITDIA_Normal_20SPD_34w_100 <-  filter_pep(LITDIA_Normal_20SPD_34w_100)
LITDIA_Normal_20SPD_40w_100 <-  filter_pep(LITDIA_Normal_20SPD_40w_100)
LITDIA_Normal_20SPD_45w_100 <-  filter_pep(LITDIA_Normal_20SPD_45w_100)
```

40 SPD 
1 ng
```{r}
LITDIA_Normal_34w_1 <-  filter_pep(LITDIA_Normal_34w_1)
LITDIA_Normal_40w_1 <-  filter_pep(LITDIA_Normal_40w_1)
LITDIA_Normal_45w_1 <-  filter_pep(LITDIA_Normal_45w_1)
```

100 ng
```{r}
LITDIA_Normal_34w_100 <-  filter_pep(LITDIA_Normal_34w_100)
LITDIA_Normal_40w_100 <-  filter_pep(LITDIA_Normal_40w_100)
LITDIA_Normal_45w_100 <-  filter_pep(LITDIA_Normal_45w_100)
```

## Number of identified peptides

Empty vectors are created to store the number of identified peptides in each replicates for each data-set.

```{r}
id_LITDIA_Normal_20SPD_34w_1 <- id_LITDIA_Normal_20SPD_40w_1 <-
  id_LITDIA_Normal_20SPD_45w_1 <- 
  id_LITDIA_Normal_20SPD_34w_100 <- id_LITDIA_Normal_20SPD_40w_100 <- id_LITDIA_Normal_20SPD_45w_100 <- id_LITDIA_Normal_34w_1 <- id_LITDIA_Normal_40w_1 <- id_LITDIA_Normal_45w_1 <- 
  id_LITDIA_Normal_34w_100 <- id_LITDIA_Normal_40w_100 <- id_LITDIA_Normal_45w_100 <- rep(NA, 4)
```

The numbers of identified peptides are counted by summing non-missing values for each replicate and stored in the vectors created above.

20 SPD 
1 ng
```{r}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_34w_1[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_34w_1[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_20SPD_40w_1[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_40w_1[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_20SPD_45w_1[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_45w_1[, i]))}
```

100 ng
```{r}
for(i in 2:5){
  id_LITDIA_Normal_20SPD_34w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_34w_100[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_20SPD_40w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_40w_100[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_20SPD_45w_100[i-1] <- sum(!is.na(LITDIA_Normal_20SPD_45w_100[, i]))}
```

40 SPD 
1 ng
```{r}
for(i in 2:5){
  id_LITDIA_Normal_34w_1[i-1] <- sum(!is.na(LITDIA_Normal_34w_1[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_40w_1[i-1] <- sum(!is.na(LITDIA_Normal_40w_1[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_45w_1[i-1] <- sum(!is.na(LITDIA_Normal_45w_1[, i]))}
```

100 ng
```{r}
for(i in 2:5){
  id_LITDIA_Normal_34w_100[i-1] <- sum(!is.na(LITDIA_Normal_34w_100[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_40w_100[i-1] <- sum(!is.na(LITDIA_Normal_40w_100[, i]))}

for(i in 2:5){
  id_LITDIA_Normal_45w_100[i-1] <- sum(!is.na(LITDIA_Normal_45w_100[, i]))}
```

# Compute CV

The function `compute_CV()` below takes the data-sets, already filtered by `filter_pep()`, as an entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our data-sets contain 4 replicates but some contains only 3. In this case, an empty column is added as a 4th replicate to keep the same format for every data-set.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

Information about the method, the number of samples per day and the input are included afterwards.

20 SPD

```{r}
LITDIA_Normal_20SPD_34w_1_cv <- compute_CV(LITDIA_Normal_20SPD_34w_1)
LITDIA_Normal_20SPD_34w_1_cv$method <- "34w"
LITDIA_Normal_20SPD_34w_1_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_34w_1_cv$input<- "1 ng"

LITDIA_Normal_20SPD_34w_100_cv <- compute_CV(LITDIA_Normal_20SPD_34w_100)
LITDIA_Normal_20SPD_34w_100_cv$method <- "34w"
LITDIA_Normal_20SPD_34w_100_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_34w_100_cv$input<- "100 ng"

LITDIA_Normal_20SPD_40w_1_cv <- compute_CV(LITDIA_Normal_20SPD_40w_1)
LITDIA_Normal_20SPD_40w_1_cv$method <- "40w"
LITDIA_Normal_20SPD_40w_1_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_40w_1_cv$input<- "1 ng"

LITDIA_Normal_20SPD_40w_100_cv <- compute_CV(LITDIA_Normal_20SPD_40w_100)
LITDIA_Normal_20SPD_40w_100_cv$method <- "40w"
LITDIA_Normal_20SPD_40w_100_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_40w_100_cv$input<- "100 ng"

LITDIA_Normal_20SPD_45w_1_cv <- compute_CV(LITDIA_Normal_20SPD_45w_1)
LITDIA_Normal_20SPD_45w_1_cv$method <- "45w"
LITDIA_Normal_20SPD_45w_1_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_45w_1_cv$input<- "1 ng"

LITDIA_Normal_20SPD_45w_100_cv <- compute_CV(LITDIA_Normal_20SPD_45w_100)
LITDIA_Normal_20SPD_45w_100_cv$method <- "45w"
LITDIA_Normal_20SPD_45w_100_cv$spd<- "20SPD"
LITDIA_Normal_20SPD_45w_100_cv$input<- "100 ng"
```

40 SPD

```{r}
LITDIA_Normal_34w_1_cv <- compute_CV(LITDIA_Normal_34w_1)
LITDIA_Normal_34w_1_cv$method <- "34w"
LITDIA_Normal_34w_1_cv$spd<- "40SPD"
LITDIA_Normal_34w_1_cv$input<- "1 ng"


LITDIA_Normal_34w_100_cv <- compute_CV(LITDIA_Normal_34w_100)
LITDIA_Normal_34w_100_cv$method <- "34w"
LITDIA_Normal_34w_100_cv$spd<- "40SPD"
LITDIA_Normal_34w_100_cv$input<- "100 ng"

LITDIA_Normal_40w_1_cv <- compute_CV(LITDIA_Normal_40w_1)
LITDIA_Normal_40w_1_cv$method <- "40w"
LITDIA_Normal_40w_1_cv$spd<- "40SPD"
LITDIA_Normal_40w_1_cv$input<- "1 ng"

LITDIA_Normal_40w_100_cv <- compute_CV(LITDIA_Normal_40w_100)
LITDIA_Normal_40w_100_cv$method <- "40w"
LITDIA_Normal_40w_100_cv$spd<- "40SPD"
LITDIA_Normal_40w_100_cv$input<- "100 ng"

LITDIA_Normal_45w_1_cv <- compute_CV(LITDIA_Normal_45w_1)
LITDIA_Normal_45w_1_cv$method <- "45w"
LITDIA_Normal_45w_1_cv$spd<- "40SPD"
LITDIA_Normal_45w_1_cv$input<- "1 ng"

LITDIA_Normal_45w_100_cv <- compute_CV(LITDIA_Normal_34w_100)
LITDIA_Normal_45w_100_cv$method <- "45w"
LITDIA_Normal_45w_100_cv$spd<- "40SPD"
LITDIA_Normal_45w_100_cv$input<- "100 ng"
```

# Join

Data frames containing CV are combined with the function `rbind()`.

```{r}
join_fig2 <- 
  rbind(LITDIA_Normal_20SPD_34w_1_cv, LITDIA_Normal_20SPD_34w_100_cv, 
        LITDIA_Normal_20SPD_40w_1_cv, LITDIA_Normal_20SPD_40w_100_cv, 
        LITDIA_Normal_20SPD_45w_1_cv, LITDIA_Normal_20SPD_45w_100_cv, 
        LITDIA_Normal_34w_1_cv, LITDIA_Normal_34w_100_cv, 
        LITDIA_Normal_40w_1_cv, LITDIA_Normal_40w_100_cv, 
        LITDIA_Normal_45w_1_cv, LITDIA_Normal_45w_100_cv)
join_fig2$method %>% table()
join_fig2$input %>% table()
join_fig2$spd %>% table()

# Factorise to set order
join_fig2$method <- factor(join_fig2$method, 
                          levels = unique(join_fig2$method))

join_fig2$input <- factor(join_fig2$input, 
                          levels = unique(join_fig2$input))

join_fig2$spd <- factor(join_fig2$spd, 
                          levels = unique(join_fig2$spd))
```

A new column called "CV_filter" is added to identify peptides with a CV over 0.15 (1), between 0.1 and 0.15 (2) and under 0.1 (3).

```{r}
join_fig2$CV_filter <- NA
join_fig2$CV_filter[join_fig2$CV < 0.1] <- "3"
join_fig2$CV_filter[join_fig2$CV >= 0.1 & join_fig2$CV <= 0.15] <- "2"
join_fig2$CV_filter[join_fig2$CV > 0.15] <- "1"
```

Peptides without CV (found in just one replicate) are filtered out. The number of identified peptides for each replicate and each CV_filter is calculated by summing the number of non-missing peptides. The mean and the standard deviation of the replicates are also calculated for each method.

```{r}
join_fig2 <- join_fig2 %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(method, spd, input, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))

join_fig2$id_S4[join_fig2$id_S4 == 0] <- NA 
join_fig2$mean_id <- rowMeans(join_fig2[5:8], na.rm = TRUE)
join_fig2$sd_id <- apply(join_fig2[5:8], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

# Plot

The mean and the standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using `ggplot2`. Error bars representing the standard deviation are displayed using `geom_errorbar()`. Due to the "stacked" aspect of the col plot, error bars y position is ajusted by using the y_errorbar variable instead of the mean_id.

```{r}
join_fig2$y_errorbar <- join_fig2$mean_id
join_fig2$y_errorbar[join_fig2$CV_filter == "1"] <-
  join_fig2$y_errorbar[join_fig2$CV_filter == "1"] +
  join_fig2$y_errorbar[join_fig2$CV_filter == "2"]+
  join_fig2$y_errorbar[join_fig2$CV_filter == "3"]
join_fig2$y_errorbar[join_fig2$CV_filter == "2"] <-
  join_fig2$y_errorbar[join_fig2$CV_filter == "2"]+
  join_fig2$y_errorbar[join_fig2$CV_filter == "3"]

figure2 <- join_fig2 %>% 
  ggplot(aes(x = method, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
 facet_grid(input~spd)+
  labs(x = "Number of Windows",
       y = "Identified peptides",
       fill = "CV") +
  theme_bw() +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        legend.title = element_text(size = 27),
        axis.title.x = element_text(vjust = 0.2),
        legend.text = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"))+
  scale_fill_manual(values = c("grey82", "#FF9090", "#FF3030"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 16000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)
```

Figure 2 is saved as a PDF.

```{r}
cairo_pdf(filename = "fig2.pdf", width = 20.83, height = 14.58)
figure2
dev.off()
```

# Session information

```{r, echo = FALSE}
sessionInfo()
```
