---
title: "Figure1"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
    fig_width: 9
    fig_height : 7
    df_print: paged
    number_sections: true
    fig_crop: no
---

Figure 1. Comparison between an Orbitrap Mass Analyser and Linear Ion Trap Mass Analyser on low-input proteomics.

# Load packages
```{r, message = FALSE}
library("tidyverse")
library("ggpubr")
library("patchwork")
library("ggpointdensity")
```

# Load data

The path to every folder used is stored to keep everything compact.
LIT data is stored in the folder located in lit_path and OT data in ot_path.

```{r, echo = FALSE}
lit_path <- 
  "C://Users/samgr/OneDrive - UCL/Documents/Internship/Data/LITDIA/LIT/"
ot_path <- 
  "C://Users/samgr/OneDrive - UCL/Documents/Internship/Data/LITDIA/OT/"
```

```{r}
#lit_path <-"C:/Users/lukwolt/Documents/R/LIT/"
#ot_path <-"C:/Users/lukwolt/Documents/R/OT/"
```

Data tables were exported from Spectronaut in csv files and need to be loaded in R.

LIT Turbo DIA
```{r}
LITDIA_Turbo_1 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Turbo_100 <- read.csv2(paste0(lit_path, "20220502_LIT_Turbo_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

LIT Rapid DIA
```{r}
LITDIA_Rapid_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Rapid_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Rapid_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Rapid_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

LIT Normal DIA
```{r}
LITDIA_Normal_1 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_1ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_5 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_5ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_10 <- read.csv2(paste0(lit_path, "20220502_LIT_Normal_DIA_10ng_40SPD_whisper100_1CV_auto.csv"))
LITDIA_Normal_100 <- read.csv2(paste0(lit_path, "20220421_LIT_Normal_DIA_100ng_40SPD_whisper100_1CV_auto.csv"))
```

OT 7.5k DIA
```{r}
OTDIA_7k_1 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_5 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_10 <- read.csv2(paste0(ot_path, "20220502_OT_7k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_7k_100 <- read.csv2(paste0(ot_path, "20220421_OT_7k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

OT 15k DIA
```{r}
OTDIA_15k_1 <- read.csv2(paste0(ot_path, "20220421_OT_15k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_5 <- read.csv2(paste0(ot_path, "20220509_OT_15k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_10 <- read.csv2(paste0(ot_path, "20220502_OT_15k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_15k_100 <- read.csv2(paste0(ot_path, "20220425_OT_15k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

OT 30k DIA
```{r}
OTDIA_30k_1 <- read.csv2(paste0(ot_path, "20220421_OT_30k_DIA_1ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_5 <- read.csv2(paste0(ot_path, "20220509_OT_30k_DIA_5ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_10 <- read.csv2(paste0(ot_path, "20220502_OT_30k_DIA_10ng_40SPD_whisper100_1CV.csv"))
OTDIA_30k_100 <- read.csv2(paste0(ot_path, "20220425_OT_30k_DIA_100ng_40SPD_whisper100_1CV.csv"))
```

# Clean data tables

Imported tables contain a lot of informations which are not usefull for our analysis. The fonction below only keep the file names (replicates), quantitatives values for each file name and the petide sequence. It also calculates the mean between replicates.
Spectronaut does some imputation by default but we want to keep missing values. Imputed values are replaced by NA.
Peptides missing in more than 1 replicates are highlighted (TRUE) in the "filtered" column 

```{r}
filter_pep <- function(x) {
  x$FG.Quantity[as.logical(x$EG.IsImputed)] <- NA
  y <- x %>% 
  group_by(R.FileName, PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity, na.rm = TRUE)) %>%  
  pivot_wider(names_from = R.FileName, 
              values_from = mean_quantity) %>%
    suppressMessages()
  z <- y %>% 
  mutate(na_nbr = rowSums(is.na(y[-1]))) %>%
  mutate(mean_quantity = rowMeans(y[2:ncol(y)], na.rm = TRUE)) %>%
  mutate(filtered = !na_nbr <= 1) %>% 
  select(-na_nbr) %>% 
  suppressMessages("`summarise()` has grouped output by 'R.FileName'. You can override using the `.groups` argument.")
  message("
Highlighted ", sum(z$filtered) , " peptide(s) found in less than ", ncol(y) -2, " replicates")
  
  return(z)
}
```

The filter_pep function is run on every dataset. A "filter" dataset were peptides missing in more than 1 replicate are removed is also created.

1 ng
```{r}
OTDIA_7k_1 <-  filter_pep(OTDIA_7k_1)
OTDIA_7k_1_filter <- OTDIA_7k_1[OTDIA_7k_1$filtered == FALSE,]

OTDIA_15k_1 <-  filter_pep(OTDIA_15k_1)
OTDIA_15k_1_filter <- OTDIA_15k_1[OTDIA_15k_1$filtered == FALSE,]

OTDIA_30k_1 <-  filter_pep(OTDIA_30k_1)
OTDIA_30k_1_filter <- OTDIA_30k_1[OTDIA_30k_1$filtered == FALSE,]

LITDIA_Turbo_1 <- filter_pep(LITDIA_Turbo_1)
LITDIA_Turbo_1_filter <- LITDIA_Turbo_1[LITDIA_Turbo_1$filtered == FALSE,]

LITDIA_Rapid_1 <- filter_pep(LITDIA_Rapid_1)
LITDIA_Rapid_1_filter <- LITDIA_Rapid_1[LITDIA_Rapid_1$filtered == FALSE,]

LITDIA_Normal_1 <- filter_pep(LITDIA_Normal_1)
LITDIA_Normal_1_filter <- LITDIA_Normal_1[LITDIA_Normal_1$filtered == FALSE,]
```

5 ng
```{r}
OTDIA_7k_5 <-  filter_pep(OTDIA_7k_5)
OTDIA_7k_5_filter <- OTDIA_7k_5[OTDIA_7k_5$filtered == FALSE,]

OTDIA_15k_5 <-  filter_pep(OTDIA_15k_5)
OTDIA_15k_5_filter <- OTDIA_15k_5[OTDIA_15k_5$filtered == FALSE,]

OTDIA_30k_5 <-  filter_pep(OTDIA_30k_5)
OTDIA_30k_5_filter <- OTDIA_30k_5[OTDIA_30k_5$filtered == FALSE,]

LITDIA_Turbo_5 <- filter_pep(LITDIA_Turbo_5)
LITDIA_Turbo_5_filter <- LITDIA_Turbo_5[LITDIA_Turbo_5$filtered == FALSE,]

LITDIA_Rapid_5 <- filter_pep(LITDIA_Rapid_5)
LITDIA_Rapid_5_filter <- LITDIA_Rapid_5[LITDIA_Rapid_5$filtered == FALSE,]

LITDIA_Normal_5 <- filter_pep(LITDIA_Normal_5)
LITDIA_Normal_5_filter <- LITDIA_Normal_5[LITDIA_Normal_5$filtered == FALSE,]
```

10 ng
```{r}
OTDIA_7k_10 <-  filter_pep(OTDIA_7k_10)
OTDIA_7k_10_filter <- OTDIA_7k_10[OTDIA_7k_10$filtered == FALSE,]

OTDIA_15k_10 <-  filter_pep(OTDIA_15k_10)
OTDIA_15k_10_filter <- OTDIA_15k_10[OTDIA_15k_10$filtered == FALSE,]

OTDIA_30k_10 <-  filter_pep(OTDIA_30k_10)
OTDIA_30k_10_filter <- OTDIA_30k_10[OTDIA_30k_10$filtered == FALSE,]

LITDIA_Turbo_10 <- filter_pep(LITDIA_Turbo_10)
LITDIA_Turbo_10_filter <- LITDIA_Turbo_10[LITDIA_Turbo_10$filtered == FALSE,]

LITDIA_Rapid_10 <- filter_pep(LITDIA_Rapid_10)
LITDIA_Rapid_10_filter <- LITDIA_Rapid_10[LITDIA_Rapid_10$filtered == FALSE,]

LITDIA_Normal_10 <- filter_pep(LITDIA_Normal_10)
LITDIA_Normal_10_filter <- LITDIA_Normal_10[LITDIA_Normal_10$filtered == FALSE,]
```

100 ng
```{r}
OTDIA_7k_100 <-  filter_pep(OTDIA_7k_100)
OTDIA_7k_100_filter <- OTDIA_7k_100[OTDIA_7k_100$filtered == FALSE,]

OTDIA_15k_100 <-  filter_pep(OTDIA_15k_100)
OTDIA_15k_100_filter <- OTDIA_15k_100[OTDIA_15k_100$filtered == FALSE,]

OTDIA_30k_100 <-  filter_pep(OTDIA_30k_100)
OTDIA_30k_100_filter <- OTDIA_30k_100[OTDIA_30k_100$filtered == FALSE,]

LITDIA_Turbo_100 <- filter_pep(LITDIA_Turbo_100)
LITDIA_Turbo_100_filter <- LITDIA_Turbo_100[LITDIA_Turbo_100$filtered == FALSE,]

LITDIA_Rapid_100 <- filter_pep(LITDIA_Rapid_100)
LITDIA_Rapid_100_filter <- LITDIA_Rapid_100[LITDIA_Rapid_100$filtered == FALSE,]

LITDIA_Normal_100 <- filter_pep(LITDIA_Normal_100)
LITDIA_Normal_100_filter <- LITDIA_Normal_100[LITDIA_Normal_100$filtered == FALSE,]
```

# Figure A

Comparison of the number of identified peptides in serial dilution (1-,5-,10-, and 100 ng) of HeLa tryptic digested between DIA-OT-based methods with different resolution scans (7.5k, 15k, and 30k) and DIA-LIT-based methods with different scanning modes (Turbo, Rapid, Normal on 40 SPD).

## Number of identified peptides

Empty vectors which will stored the number of identified peptides in each replicates for each dataset are created.

```{r}
id_LITDIA_Turbo_1 <- id_LITDIA_Turbo_5 <- 
  id_LITDIA_Turbo_10 <- id_LITDIA_Turbo_100 <- 
  id_LITDIA_Rapid_1 <- id_LITDIA_Rapid_5 <- 
  id_LITDIA_Rapid_10 <- id_LITDIA_Rapid_100 <-
  id_LITDIA_Normal_1 <- id_LITDIA_Normal_5 <- 
  id_LITDIA_Normal_10 <- id_LITDIA_Normal_100 <-  
  id_OTDIA_7k_1 <- id_OTDIA_7k_5 <- 
  id_OTDIA_7k_10 <- id_OTDIA_7k_100 <- 
  id_OTDIA_15k_1 <- id_OTDIA_15k_5 <- 
  id_OTDIA_15k_10 <- id_OTDIA_15k_100 <- 
  id_OTDIA_30k_1 <- id_OTDIA_30k_5 <- 
  id_OTDIA_30k_10 <- id_OTDIA_30k_100 <- rep(NA, 4)
```

Number of id are obtained by excecuting the sum of each non-missing values for each column corresponding to a replicate.

### 1 ng

OT
```{r}
for(i in 2:5){
  id_OTDIA_7k_1[i-1] <- sum(!is.na(OTDIA_7k_1[, i]))}

for(i in 2:5){
  id_OTDIA_15k_1[i-1] <- sum(!is.na(OTDIA_15k_1[, i]))}

for(i in 2:5){
  id_OTDIA_30k_1[i-1] <- sum(!is.na(OTDIA_30k_1[, i]))}
```

LIT
```{r}
for(i in 2:5){
id_LITDIA_Turbo_1[i-1] <- sum(!is.na(LITDIA_Turbo_1[, i]))}

for(i in 2:5){
id_LITDIA_Rapid_1[i-1] <- sum(!is.na(LITDIA_Rapid_1[, i]))}

for(i in 2:5){
id_LITDIA_Normal_1[i-1] <- sum(!is.na(LITDIA_Normal_1[, i]))}
```
 
### 5 ng

OT
```{r}
for(i in 2:5){
  id_OTDIA_7k_5[i-1] <- sum(!is.na(OTDIA_7k_5[, i]))}

for(i in 2:5){
  id_OTDIA_15k_5[i-1] <- sum(!is.na(OTDIA_15k_5[, i]))}

for(i in 2:5){
  id_OTDIA_30k_5[i-1] <- sum(!is.na(OTDIA_30k_5[, i]))}
```

LIT
```{r}
for(i in 2:5){
id_LITDIA_Turbo_5[i-1] <- sum(!is.na(LITDIA_Turbo_5[, i]))}

for(i in 2:5){
id_LITDIA_Rapid_5[i-1] <- sum(!is.na(LITDIA_Rapid_5[, i]))}

for(i in 2:5){
id_LITDIA_Normal_5[i-1] <- sum(!is.na(LITDIA_Normal_5[, i]))}
```

### 10 ng

OT
```{r}
for(i in 2:5){
  id_OTDIA_7k_10[i-1] <- sum(!is.na(OTDIA_7k_10[, i]))}

for(i in 2:5){
  id_OTDIA_15k_10[i-1] <- sum(!is.na(OTDIA_15k_10[, i]))}

for(i in 2:5){
  id_OTDIA_30k_10[i-1] <- sum(!is.na(OTDIA_30k_10[, i]))}
```

LIT Turbo DIA auto
```{r}
for(i in 2:5){
id_LITDIA_Turbo_10[i-1] <- sum(!is.na(LITDIA_Turbo_10[, i]))}

for(i in 2:5){
id_LITDIA_Rapid_10[i-1] <- sum(!is.na(LITDIA_Rapid_10[, i]))}

for(i in 2:5){
id_LITDIA_Normal_10[i-1] <- sum(!is.na(LITDIA_Normal_10[, i]))}
```

### 100 ng

OT
```{r}
for(i in 2:5){
  id_OTDIA_7k_100[i-1] <- sum(!is.na(OTDIA_7k_100[, i]))}

for(i in 2:5){
  id_OTDIA_15k_100[i-1] <- sum(!is.na(OTDIA_15k_100[, i]))}

for(i in 2:5){
  id_OTDIA_30k_100[i-1] <- sum(!is.na(OTDIA_30k_100[, i]))}
```

LIT
```{r}
for(i in 2:5){
id_LITDIA_Turbo_100[i-1] <- sum(!is.na(LITDIA_Turbo_100[, i]))}

for(i in 2:5){
id_LITDIA_Rapid_100[i-1] <- sum(!is.na(LITDIA_Rapid_100[, i]))}

for(i in 2:5){
id_LITDIA_Normal_100[i-1] <- sum(!is.na(LITDIA_Normal_100[, i]))}
```

## Join A

Number of identified peptides for each files are combined into a data frame containing information about the method (OT resolution and LIT scanning mode), the replicate and the input.

```{r}
id_pep <- data.frame(method = rep(c(rep("OT 7.5k", 4), rep("OT 15k", 4), rep("OT 30k", 4),
                                    rep("LIT Turbo", 4), rep("LIT Rapid", 4), rep("LIT Normal", 4)), 4),
           replicate = rep(1:4, 24),
           id = c(id_OTDIA_7k_1, id_OTDIA_15k_1, id_OTDIA_30k_1, 
                  id_LITDIA_Turbo_1, id_LITDIA_Rapid_1, id_LITDIA_Normal_1,
                  id_OTDIA_7k_5, id_OTDIA_15k_5, id_OTDIA_30k_5, 
                  id_LITDIA_Turbo_5, id_LITDIA_Rapid_5, id_LITDIA_Normal_5,
                  id_OTDIA_7k_10, id_OTDIA_15k_10, id_OTDIA_30k_10, 
                  id_LITDIA_Turbo_10, id_LITDIA_Rapid_10, id_LITDIA_Normal_10,
                  id_OTDIA_7k_100, id_OTDIA_15k_100, id_OTDIA_30k_100, 
                  id_LITDIA_Turbo_100, id_LITDIA_Rapid_100, id_LITDIA_Normal_100),
           input = c(rep("1 ng", 24), rep("5 ng", 24), rep("10 ng", 24), rep("100 ng", 24)))

# Factorise to set order
id_pep$method <- factor(id_pep$method, levels = unique(id_pep$method))
id_pep$input <- factor(id_pep$input, levels = unique(id_pep$input))
```

## Plot A

The mean and standard deviation is calcutated for the replicates of each method and are plotted in a line plot using ggplot.

```{r}
figure1a <- id_pep %>% 
  group_by(method, input) %>% 
  summarise(mean_id = mean(id),
            sd_id = sd(id))%>%
  ggplot(aes(x = input, y = mean_id, group = method, color = method))+
  theme_bw()+
  geom_line(size = 2.5)+
  geom_point(size = 4)+
  scale_color_manual(values = c("#ADC2E8", "#7F9FDB", "#527DCE", "#EEB9CF", "#DF7FA7", "#D35087"))+
  geom_errorbar(aes(ymin = mean_id - sd_id, 
                         ymax = mean_id + sd_id),
                    width = 0.1,
                    size = 1.5)+
  labs(color = "Methods",
       x = "Input",
       y = "Identified peptides",
       title = "A")+
  theme(legend.position = c(0.23, 0.85),
        legend.background = element_blank(),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        legend.key.size = unit(0.9, "cm"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1))
figure1a
```

# Figure B

Comparison of identified peptides between the DIA-OT-based methods and the DIA-LIT-based methods. Identified peptides with a coefficient of variation (CV) between 10% and 15% are colored with light red and those with a CV below 10 % with dark red.

## Compute CV

The function below takes the clean datasets for entry and compute the coefficient of variation (CV) for the replicates of each method. Most of our datasets contain 4 replicates but some contains only 3. If this is the case, a empty column is added for the CV of a 4th replicate so that each dataset keep the same format.

```{r}
compute_CV <- function(x){
  y <- x %>% 
    mutate(sd = apply(x[, 2:(ncol(x)-2)],
                      FUN = sd, MARGIN =  1, na.rm = TRUE),
           CV = sd/mean_quantity)
  colnames(y)[2:(ncol(x)-2)] <- paste0("S", 1:(ncol(x)-3))
  if(ncol(x) <= 6){
  y$S4 <- NA
 }
  return(y)
}
```

information about the method and the input are added afterward.

### 1 ng

LIT
```{r}
LITDIA_Turbo_1_CV <- compute_CV(LITDIA_Turbo_1)
LITDIA_Turbo_1_CV$method <- "LIT Turbo"
LITDIA_Turbo_1_CV$input<- "1 ng"

LITDIA_Rapid_1_CV <- compute_CV(LITDIA_Rapid_1)
LITDIA_Rapid_1_CV$method <- "LIT Rapid"
LITDIA_Rapid_1_CV$input<- "1 ng"

LITDIA_Normal_1_CV <- compute_CV(LITDIA_Normal_1)
LITDIA_Normal_1_CV$method <- "LIT Normal"
LITDIA_Normal_1_CV$input<- "1 ng"
```

OT
```{r}
OTDIA_7k_1_CV <- compute_CV(OTDIA_7k_1)
OTDIA_7k_1_CV$method <- "OT 7k"
OTDIA_7k_1_CV$input<- "1 ng"

OTDIA_15k_1_CV <- compute_CV(OTDIA_15k_1)
OTDIA_15k_1_CV$method <- "OT 15k"
OTDIA_15k_1_CV$input<- "1 ng"

OTDIA_30k_1_CV <- compute_CV(OTDIA_30k_1)
OTDIA_30k_1_CV$method <- "OT 30k"
OTDIA_30k_1_CV$input<- "1 ng"
```

### 5 ng

LIT
```{r}
LITDIA_Turbo_5_CV <- compute_CV(LITDIA_Turbo_5)
LITDIA_Turbo_5_CV$method <- "LIT Turbo"
LITDIA_Turbo_5_CV$input<- "5 ng"

LITDIA_Rapid_5_CV <- compute_CV(LITDIA_Rapid_5)
LITDIA_Rapid_5_CV$method <- "LIT Rapid"
LITDIA_Rapid_5_CV$input<- "5 ng"

LITDIA_Normal_5_CV <- compute_CV(LITDIA_Normal_5)
LITDIA_Normal_5_CV$method <- "LIT Normal"
LITDIA_Normal_5_CV$input<- "5 ng"
```

OT
```{r}
OTDIA_7k_5_CV <- compute_CV(OTDIA_7k_5)
OTDIA_7k_5_CV$method <- "OT 7k"
OTDIA_7k_5_CV$input<- "5 ng"

OTDIA_15k_5_CV <- compute_CV(OTDIA_15k_5)
OTDIA_15k_5_CV$method <- "OT 15k"
OTDIA_15k_5_CV$input<- "5 ng"

OTDIA_30k_5_CV <- compute_CV(OTDIA_30k_5)
OTDIA_30k_5_CV$method <- "OT 30k"
OTDIA_30k_5_CV$input<- "5 ng"
```

### 10 ng

LIT
```{r}
LITDIA_Turbo_10_CV <- compute_CV(LITDIA_Turbo_10)
LITDIA_Turbo_10_CV$method <- "LIT Turbo"
LITDIA_Turbo_10_CV$input<- "10 ng"

LITDIA_Rapid_10_CV <- compute_CV(LITDIA_Rapid_10)
LITDIA_Rapid_10_CV$method <- "LIT Rapid"
LITDIA_Rapid_10_CV$input<- "10 ng"

LITDIA_Normal_10_CV <- compute_CV(LITDIA_Normal_10)
LITDIA_Normal_10_CV$method <- "LIT Normal"
LITDIA_Normal_10_CV$input<- "10 ng"
```

OT
```{r}
OTDIA_7k_10_CV <- compute_CV(OTDIA_7k_10)
OTDIA_7k_10_CV$method <- "OT 7k"
OTDIA_7k_10_CV$input<- "10 ng"

OTDIA_15k_10_CV <- compute_CV(OTDIA_15k_10)
OTDIA_15k_10_CV$method <- "OT 15k"
OTDIA_15k_10_CV$input<- "10 ng"

OTDIA_30k_10_CV <- compute_CV(OTDIA_30k_10)
OTDIA_30k_10_CV$method <- "OT 30k"
OTDIA_30k_10_CV$input<- "10 ng"
```

### 100 ng

LIT
```{r}
LITDIA_Turbo_100_CV <- compute_CV(LITDIA_Turbo_100)
LITDIA_Turbo_100_CV$method <- "LIT Turbo"
LITDIA_Turbo_100_CV$input<- "100 ng"

LITDIA_Rapid_100_CV <- compute_CV(LITDIA_Rapid_100)
LITDIA_Rapid_100_CV$method <- "LIT Rapid"
LITDIA_Rapid_100_CV$input<- "100 ng"

LITDIA_Normal_100_CV <- compute_CV(LITDIA_Normal_100)
LITDIA_Normal_100_CV$method <- "LIT Normal"
LITDIA_Normal_100_CV$input<- "100 ng"
```

OT
```{r}
OTDIA_7k_100_CV <- compute_CV(OTDIA_7k_100)
OTDIA_7k_100_CV$method <- "OT 7k"
OTDIA_7k_100_CV$input<- "100 ng"

OTDIA_15k_100_CV <- compute_CV(OTDIA_15k_100)
OTDIA_15k_100_CV$method <- "OT 15k"
OTDIA_15k_100_CV$input<- "100 ng"

OTDIA_30k_100_CV <- compute_CV(OTDIA_30k_100)
OTDIA_30k_100_CV$method <- "OT 30k"
OTDIA_30k_100_CV$input<- "100 ng"
```

## Join B

Data frames containing CV are combined.

```{r}
CV_joined <- 
  rbind(LITDIA_Turbo_1_CV, LITDIA_Rapid_1_CV, LITDIA_Normal_1_CV,
      OTDIA_7k_1_CV, OTDIA_15k_1_CV, OTDIA_30k_1_CV,
      LITDIA_Turbo_5_CV, LITDIA_Rapid_5_CV, LITDIA_Normal_5_CV,
      OTDIA_7k_5_CV, OTDIA_15k_5_CV, OTDIA_30k_5_CV,
      LITDIA_Turbo_10_CV, LITDIA_Rapid_10_CV, LITDIA_Normal_10_CV,
      OTDIA_7k_10_CV, OTDIA_15k_10_CV, OTDIA_30k_10_CV,
      LITDIA_Turbo_100_CV, LITDIA_Rapid_100_CV, LITDIA_Normal_100_CV,
      OTDIA_7k_100_CV, OTDIA_15k_100_CV, OTDIA_30k_100_CV)

CV_joined$method %>% table()
CV_joined$input %>% table()

# Factorise to set order
CV_joined$method <- factor(CV_joined$method, 
                          levels = unique(CV_joined$method))
CV_joined$input <- factor(CV_joined$input, 
                          levels = unique(CV_joined$input))
````

A new column calld "CV_filter" is added to identify peptides with CV >= 15 (1), CV between 0.1 et 0.15 (2) and CV > 0.1 (3)

```{r}
CV_joined$CV_filter <- NA
CV_joined$CV_filter[CV_joined$CV < 0.1] <- "3"
CV_joined$CV_filter[CV_joined$CV >= 0.1 & CV_joined$CV <= 0.15] <- "2"
CV_joined$CV_filter[CV_joined$CV > 0.15] <- "1"
```

Peptides without CV (found in only one replicates) are filtered out and the number of identified peptide for each replicates and CV_filter is calculated but summing the number of non-missing peptides.
The mean and standard deviation of replicates is also calculated for each method.

```{r, message=FALSE}
CV_joined <- CV_joined %>%
  filter(!is.na(CV_filter)) %>% 
  group_by(method, input, CV_filter) %>% 
  summarise(id_S1 = sum(!is.na(S1)),
            id_S2 = sum(!is.na(S2)),
            id_S3 = sum(!is.na(S3)),
            id_S4 = sum(!is.na(S4)))

CV_joined$mean_id <- rowMeans(CV_joined[4:7], na.rm = TRUE)
CV_joined$sd_id <- apply(CV_joined[4:7], FUN =  sd, MARGIN = 1, na.rm = TRUE)
```

## Plot B

The mean and standard deviation of identified peptides for each CV_filter and method are plotted in a stacked col plot using ggplot.

```{r}
CV_joined$y_errorbar <- CV_joined$mean_id
CV_joined$y_errorbar[CV_joined$CV_filter == "1"] <- 
  CV_joined$y_errorbar[CV_joined$CV_filter == "1"] +
  CV_joined$y_errorbar[CV_joined$CV_filter == "2"]+
  CV_joined$y_errorbar[CV_joined$CV_filter == "3"]
CV_joined$y_errorbar[CV_joined$CV_filter == "2"] <-
  CV_joined$y_errorbar[CV_joined$CV_filter == "2"]+
  CV_joined$y_errorbar[CV_joined$CV_filter == "3"]
figure1b <- CV_joined %>% 
  ggplot(aes(x = input, y = mean_id, fill = CV_filter))+
  geom_col(width = 0.7) +
  facet_wrap(~method) +
  labs(x = "Input",
       y = "Identified peptides",
       fill = "CV",
       title = "B") +
  theme(axis.text = element_text(size = 24),
        axis.title = element_text(size = 27),
        strip.text = element_text(size = 27),
        strip.background = element_rect(fill = "#E5E4F7"),
        axis.title.y = element_text(vjust = 2.2),
        axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1),
        legend.title = element_text(size = 27),
        legend.text = element_text(size = 22),
        legend.key.size = unit(0.9, "cm"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.08),
        plot.margin = margin(l = 25),
        legend.position = c(0.1, 0.285),
        legend.background = element_blank())+
  scale_fill_manual(values = c("grey82", "#ff9090", "#ff3030"),
                    labels = c("\U2265 15%", "10 - 15%", "< 10%" ))+
  scale_y_continuous(limits = c(0, 18000))+
  geom_errorbar(aes(ymin = y_errorbar - sd_id, 
                         ymax = y_errorbar + sd_id),
                    width = 0.2,
                    size = 1)
 
figure1b
```

# Figure C

Pearson correlation of identified peptides between DIA-OT-based methods and DIA-LIT-based methods when 1-, 5-, 10- and 100 ng of HeLa tryptic digested were analyzed in quadruplicate.

## Join LIT and OT data frames

New data frames are created with LIT and OT quantification data for peptides found in both methods. LIT Turbo is compared with OT 7.5k, Rapid with 15k and Normal with 30k. Only peptides found in at least 3 of the 4 replicates are kept.
Informations about the methods compared and input are added.

### 1 ng

```{r}
Turbo_vs_7k_1 <- 
  inner_join(OTDIA_7k_1_filter[,c(1,6)],
             LITDIA_Turbo_1_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Turbo_vs_7k_1$method <- "LIT Turbo vs OT 7.5k"
Turbo_vs_7k_1$input <- "1 ng"

Rapid_vs_15k_1 <-  
  inner_join(OTDIA_15k_1_filter[,c(1,6)],
             LITDIA_Rapid_1_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Rapid_vs_15k_1$method <- "LIT Rapid vs OT 15k"
Rapid_vs_15k_1$input <- "1 ng"

Normal_vs_30k_1 <-  
  inner_join(OTDIA_30k_1_filter[,c(1,6)],
             LITDIA_Normal_1_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Normal_vs_30k_1$method <- "LIT Normal vs OT 30k"
Normal_vs_30k_1$input <- "1 ng"
```

### 5 ng

```{r}
Turbo_vs_7k_5 <- 
  inner_join(OTDIA_7k_5_filter[,c(1,6)],
             LITDIA_Turbo_5_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Turbo_vs_7k_5$method <- "LIT Turbo vs OT 7.5k"
Turbo_vs_7k_5$input <- "5 ng"

Rapid_vs_15k_5 <-  
  inner_join(OTDIA_15k_5_filter[,c(1,6)],
             LITDIA_Rapid_5_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Rapid_vs_15k_5$method <- "LIT Rapid vs OT 15k"
Rapid_vs_15k_5$input <- "5 ng"

Normal_vs_30k_5 <-  
  inner_join(OTDIA_30k_5_filter[,c(1,6)],
             LITDIA_Normal_5_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Normal_vs_30k_5$method <- "LIT Normal vs OT 30k"
Normal_vs_30k_5$input <- "5 ng"
```

### 10 ng
```{r}
Turbo_vs_7k_10 <- 
  inner_join(OTDIA_7k_10_filter[,c(1,6)],
             LITDIA_Turbo_10_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Turbo_vs_7k_10$method <- "LIT Turbo vs OT 7.5k"
Turbo_vs_7k_10$input <- "10 ng"

Rapid_vs_15k_10 <-  
  inner_join(OTDIA_15k_10_filter[,c(1,6)],
             LITDIA_Rapid_10_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Rapid_vs_15k_10$method <- "LIT Rapid vs OT 15k"
Rapid_vs_15k_10$input <- "10 ng"

Normal_vs_30k_10 <-  
  inner_join(OTDIA_30k_10_filter[,c(1,6)],
             LITDIA_Normal_10_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Normal_vs_30k_10$method <- "LIT Normal vs OT 30k"
Normal_vs_30k_10$input <- "10 ng"
```

### 100 ng  
```{r}
Turbo_vs_7k_100 <-  
  inner_join(OTDIA_7k_100_filter[,c(1,6)],
             LITDIA_Turbo_100_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Turbo_vs_7k_100$method <- "LIT Turbo vs OT 7.5k"
Turbo_vs_7k_100$input <- "100 ng"

Rapid_vs_15k_100 <- 
  inner_join(OTDIA_15k_100_filter[,c(1,6)],
             LITDIA_Rapid_100_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Rapid_vs_15k_100$method <- "LIT Rapid vs OT 15k"
Rapid_vs_15k_100$input <- "100 ng"

Normal_vs_30k_100 <- 
  inner_join(OTDIA_30k_100_filter[,c(1,6)],
             LITDIA_Normal_100_filter[,c(1,6)],
             by = "PEP.StrippedSequence",
             suffix = c("_OT", "_LIT"))
Normal_vs_30k_100$method <- "LIT Normal vs OT 30k"
Normal_vs_30k_100$input <- "100 ng"
```

## Join C

Comparison table are combined.

```{r}
figure1c_join <- rbind(Turbo_vs_7k_1, Rapid_vs_15k_1, Normal_vs_30k_1,
               Turbo_vs_7k_5, Rapid_vs_15k_5, Normal_vs_30k_5,
               Turbo_vs_7k_10, Rapid_vs_15k_10, Normal_vs_30k_10,
               Turbo_vs_7k_100, Rapid_vs_15k_100, Normal_vs_30k_100)

# Factorise to set order
figure1c_join$method <- factor(figure1c_join$method,
                       levels = c("LIT Turbo vs OT 7.5k",
                                  "LIT Rapid vs OT 15k",
                                  "LIT Normal vs OT 30k"))
figure1c_join$input <- factor(figure1c_join$input, 
                              levels = unique(figure1c_join$input))
```

## Plot C

LIT and OT abundances are plotted against each other in a scatter plot using ggplot. A regression line with pearson correlation coefficient is also added.

```{r}
figure1c <- figure1c_join %>% 
  ggplot(aes(x = mean_quantity_OT, y = mean_quantity_LIT)) +
  geom_pointdensity(size = 1.5)+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90,
                                   vjust = 0.3),
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.12)) +
  geom_smooth(method = lm,
              se = FALSE,
              color = "red",
              size = 1.2)+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3, color = "red",
           size = 7,
           label.x.npc = 0,
           label.y.npc = 0.9)+
  labs(x = "OT Abundance (log10)",
       y = "LIT Abundance (log10)",
       title = "C") +
  scale_y_log10(breaks = c(1000, 100000)) +
  scale_x_log10() +
  facet_grid(input~method)
labels <- paste0(c(sum(figure1c_join$method == "LIT Turbo vs OT 7.5k" & figure1c_join$input == "1 ng"),
                   sum(figure1c_join$method == "LIT Rapid vs OT 15k" & figure1c_join$input == "1 ng"),
                   sum(figure1c_join$method == "LIT Normal vs OT 30k" & figure1c_join$input == "1 ng"),
                   sum(figure1c_join$method == "LIT Turbo vs OT 7.5k" & figure1c_join$input == "5 ng"),
                   sum(figure1c_join$method == "LIT Rapid vs OT 15k" & figure1c_join$input == "5 ng"),
                   sum(figure1c_join$method == "LIT Normal vs OT 30k" & figure1c_join$input == "5 ng"),
                   sum(figure1c_join$method == "LIT Turbo vs OT 7.5k" & figure1c_join$input == "10 ng"),
                   sum(figure1c_join$method == "LIT Rapid vs OT 15k" & figure1c_join$input == "10 ng"),
                   sum(figure1c_join$method == "LIT Normal vs OT 30k" & figure1c_join$input == "10 ng"),
                   sum(figure1c_join$method == "LIT Turbo vs OT 7.5k" & figure1c_join$input == "100 ng"),
                   sum(figure1c_join$method == "LIT Rapid vs OT 15k" & figure1c_join$input == "100 ng"),
                   sum(figure1c_join$method == "LIT Normal vs OT 30k" & figure1c_join$input == "100 ng")),
                 " pep.")
data_labels <- 
  data.frame(method = as.factor(rep(c("LIT Turbo vs OT 7.5k",
                                      "LIT Rapid vs OT 15k",
                                      "LIT Normal vs OT 30k"),4)),
             input = as.factor(c(rep("1 ng",3), rep("5 ng",3),rep("10 ng",3), rep("100 ng",3))),
             label = labels)
figure1c <- figure1c +
  geom_text(x = -Inf, y = Inf,
            hjust = -0.15, vjust = 3.2,
            aes(label = labels, group = NULL), data = data_labels,
            size = 7,
            face = "bold")
figure1c
```

# Figure D

Distribution of the range of detection between the DIA-OT-based method and DIA-LIT-based methods and overlapping of identified peptides based on their intensities.

## Highlight peptdes found in OT

A new column is added to each LIT dataset to identify peptides which were also found in their corresponding OT datasets.
Informations about the scanning mode and input are added.


### 1 ng
```{r}
#Turbo
LITDIA_Turbo_1_filter$in_OT <- 
  LITDIA_Turbo_1_filter$PEP.StrippedSequence %in%
  OTDIA_7k_1_filter$PEP.StrippedSequence
LITDIA_Turbo_1_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_1_filter$in_OT <- 
  LITDIA_Rapid_1_filter$PEP.StrippedSequence %in%
  OTDIA_15k_1_filter$PEP.StrippedSequence
LITDIA_Rapid_1_filter$method <- "Rapid"
#Normal
LITDIA_Normal_1_filter$in_OT <- 
  LITDIA_Normal_1_filter$PEP.StrippedSequence %in%
  OTDIA_30k_1_filter$PEP.StrippedSequence
LITDIA_Normal_1_filter$method <- "Normal"

#Input
LITDIA_Turbo_1_filter$input <-
  LITDIA_Rapid_1_filter$input <-
  LITDIA_Normal_1_filter$input <- "1 ng"
```

### 5 ng

```{r}
#Turbo
LITDIA_Turbo_5_filter$in_OT <- 
  LITDIA_Turbo_5_filter$PEP.StrippedSequence %in%
  OTDIA_7k_5_filter$PEP.StrippedSequence
LITDIA_Turbo_5_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_5_filter$in_OT <- 
  LITDIA_Rapid_5_filter$PEP.StrippedSequence %in%
  OTDIA_15k_5_filter$PEP.StrippedSequence
LITDIA_Rapid_5_filter$method <- "Rapid"

#Normal
LITDIA_Normal_5_filter$in_OT <- 
  LITDIA_Normal_5_filter$PEP.StrippedSequence %in%
  OTDIA_30k_5_filter$PEP.StrippedSequence
LITDIA_Normal_5_filter$method <- "Normal"

#Input
LITDIA_Turbo_5_filter$input <-
  LITDIA_Rapid_5_filter$input <-
  LITDIA_Normal_5_filter$input <- "5 ng"
```

### 10 ng

```{r}
#Turbo
LITDIA_Turbo_10_filter$in_OT <- 
  LITDIA_Turbo_10_filter$PEP.StrippedSequence %in%
  OTDIA_7k_10_filter$PEP.StrippedSequence
LITDIA_Turbo_10_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_10_filter$in_OT <- 
  LITDIA_Rapid_10_filter$PEP.StrippedSequence %in%
  OTDIA_15k_10_filter$PEP.StrippedSequence
LITDIA_Rapid_10_filter$method <- "Rapid"

#Normal
LITDIA_Normal_10_filter$in_OT <- 
  LITDIA_Normal_10_filter$PEP.StrippedSequence %in%
  OTDIA_30k_10_filter$PEP.StrippedSequence
LITDIA_Normal_10_filter$method <- "Normal"

#Input
LITDIA_Turbo_10_filter$input <-
  LITDIA_Rapid_10_filter$input <-
  LITDIA_Normal_10_filter$input <- "10 ng"
```

### 100 ng

```{r}
#Turbo
LITDIA_Turbo_100_filter$in_OT <- 
  LITDIA_Turbo_100_filter$PEP.StrippedSequence %in%
  OTDIA_7k_100_filter$PEP.StrippedSequence
LITDIA_Turbo_100_filter$method <- "Turbo"

#Rapid
LITDIA_Rapid_100_filter$in_OT <- 
  LITDIA_Rapid_100_filter$PEP.StrippedSequence %in%
  OTDIA_15k_100_filter$PEP.StrippedSequence
LITDIA_Rapid_100_filter$method <- "Rapid"

#Normal
LITDIA_Normal_100_filter$in_OT <- 
  LITDIA_Normal_100_filter$PEP.StrippedSequence %in%
  OTDIA_30k_100_filter$PEP.StrippedSequence
LITDIA_Normal_100_filter$method <- "Normal"

#Input
LITDIA_Turbo_100_filter$input <-
  LITDIA_Rapid_100_filter$input <- 
  LITDIA_Normal_100_filter$input <- "100 ng"
```

## Join D

Data frames for are combined. Only relevant columns are kept.

```{r}
figure1d_join <- 
  rbind(LITDIA_Turbo_1_filter[,c(1,6:10)], LITDIA_Turbo_5_filter[,c(1,6:10)],
        LITDIA_Turbo_10_filter[,c(1,6:10)], LITDIA_Turbo_100_filter[,c(1,6:10)],
        LITDIA_Rapid_1_filter[,c(1,6:10)], LITDIA_Rapid_5_filter[,c(1,6:10)],
        LITDIA_Rapid_10_filter[,c(1,6:10)], LITDIA_Rapid_100_filter[,c(1,6:10)],
        LITDIA_Normal_1_filter[,c(1,6:10)], LITDIA_Normal_5_filter[,c(1,6:10)],
        LITDIA_Normal_10_filter[,c(1,6:10)], LITDIA_Normal_100_filter[,c(1,6:10)]) 

# Factorise to set order
figure1d_join$method <- factor(figure1d_join$method,
                       levels = unique(figure1d_join$method))
figure1d_join$input <- factor(figure1d_join$input,
                       levels = unique(figure1d_join$input))
```

## Plot D

LIT abundances for peptides found in LIT only (grey) or in both LIT and OT (red) are plotted in an histogram using ggplot.

```{r}
figure1d <- figure1d_join %>% 
  ggplot(aes(x = mean_quantity, fill = in_OT))+
  geom_histogram(bins = 40,
                 position = "identity",
                 alpha = 0.4)+
  scale_x_log10()+
  scale_y_continuous(breaks = c(0, 500, 1000)) +
  scale_fill_manual(values = c("grey20", "red"),
                    labels = c("LIT only", "LIT and OT"))+
  labs(x = "DIA-LIT Abundance (log10)",
       y = "Identified peptides",
       title = "D")+
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.3),
        legend.position = c(0.915, 0.927),
        legend.background = element_blank(),
        axis.title = element_text(size = 27),
        axis.text = element_text(size = 27),
        legend.title = element_blank(),
        legend.text = element_text(size = 24),
        strip.text.x = element_text(size = 27),
        strip.text.y = element_text(size = 27, vjust = 1.2),
        strip.background = element_rect(fill = "#E5E4F7"),
        plot.title = element_text(size = 32, face = "bold",
                                  hjust = -0.12)) +
  facet_grid(input ~ method)
labels1 <- 
  paste0(c(sum(figure1d_join$method == "Turbo" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "100 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Rapid" &  figure1d_join$input == "100 ng" & figure1d_join$in_OT == FALSE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "100 ng" & figure1d_join$in_OT == FALSE)),
         " pep.")
                       
data_labels1 <- 
  data.frame(method = as.factor(rep(c("Turbo", "Rapid", "Normal"),4)),
             input = as.factor(c(rep("1 ng",3), rep("5 ng",3), rep("10 ng",3), rep("100 ng",3))),
             label = labels1,
             in_OT = rep(FALSE, 12))
labels2<- 
  paste0(c(sum(figure1d_join$method == "Turbo" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "1 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "5 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Rapid" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "10 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Turbo" & figure1d_join$input == "100 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Rapid" &  figure1d_join$input == "100 ng" & figure1d_join$in_OT == TRUE),
           sum(figure1d_join$method == "Normal" & figure1d_join$input == "100 ng" & figure1d_join$in_OT == TRUE)),
         " pep.")
                       
data_labels2 <- 
  data.frame(method = as.factor(rep(c("Turbo", "Rapid", "Normal"),4)),
             input = as.factor(c(rep("1 ng",3), rep("5 ng",3), rep("10 ng",3), rep("100 ng",3))),
             label = labels2,
             in_OT = rep(TRUE, 12))
figure1d <- figure1d +
  geom_text(x = -Inf, y = Inf,
            hjust = -0.1, vjust = 1.82,
            aes(label = label, group = NULL), data = data_labels1,
            color = "grey50",
            size = 7,
            face = "bold")+
  geom_text(x = -Inf, y = Inf,
            hjust = -0.1, vjust = 3.32,
            aes(label = label, group = NULL), data = data_labels2,
            color = "red",
            size = 7,
            face = "bold")
figure1d
```

# Join A,B,C and D

Plot 1A, 1B, 1C and 1D are combined using patchwork to create figure 1. Fig. 1 is saved as pdf.

```{r, fig.height= 14}
temp <- figure1a +  figure1b + plot_layout(widths = c(1, 2))
temp2 <- plot_spacer() + figure1c + plot_spacer() + plot_layout(widths = c(1, 10, 1))
temp3 <- plot_spacer() + figure1d + plot_spacer() + plot_layout(widths = c(1, 10, 1))

figure1 <- temp/temp2/temp3 + plot_layout(heights = c(0.8, 1, 1))

figure1

#Save as pdf
#cairo_pdf(filename = "fig1.pdf", width = 20.83, height = 27.08)
#figure1
#dev.off()
```